\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{booktabs}
\usepackage{float}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!55!black,
  citecolor=blue!55!black,
  urlcolor=blue!60!black
}

\definecolor{codebg}{RGB}{247,248,250}
\definecolor{codecomment}{RGB}{42,112,74}
\definecolor{codekeyword}{RGB}{42,74,145}
\definecolor{codestring}{RGB}{150,66,55}

\lstdefinelanguage{Wolfram}{
  morekeywords={ClearAll,Needs,DiracTrace,DiracSimplify,DiracSigma,
    Contract,ScalarProductExpand,ExpandScalarProduct,Collect2,Simplify,
    Together,Thread,Table,Association,AssociationThread,True,False},
  sensitive=true,
  morecomment=[s]{(*}{*)},
  morestring=[b]"
}

\lstset{
  language=Wolfram,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{codekeyword},
  commentstyle=\color{codecomment},
  stringstyle=\color{codestring},
  backgroundcolor=\color{codebg},
  frame=single,
  rulecolor=\color{black!15},
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  aboveskip=0.8em,
  belowskip=0.8em
}

\newcommand{\ii}{\mathrm{i}}
\newcommand{\ee}{\mathrm{e}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\slashedk}{\not\!k}
\newcommand{\slashedp}{\not\!p}
\newcommand{\slashedpp}{\not\!p^{\prime}}
\newcommand{\slashedq}{\not\!q}
\newcommand{\Mathematica}{\textit{Mathematica}}
\newcommand{\FeynCalc}{\textsc{FeynCalc}}

\title{Independent Mathematica Derivation for\\
  $D_{s1}/B_{s1}\to D_s/B_s\,\gamma$}
\author{Ds/Bs gamma project}
\date{22 July 2026}

\begin{document}
\maketitle

\begin{abstract}
This note is a clean, independent restart of the symbolic part of the
$D_{s1}/B_{s1}\to D_s/B_s\gamma$ light-cone sum-rule calculation.  It records
exactly what has been implemented and checked in \Mathematica{} and
\FeynCalc: the currents, correlator ordering, Wick contraction, propagator
routing, Rohrwild three-point/background-field notation, hard-emission
traces, Ward identities, E1 projection,
inverse-denominator reduction, Feynman parameterization, the first soft
two-particle Fierz traces, physical-state mixing, the pure-axial Colangelo
limit, and the decay-constant normalization.  It does not import the Python
implementation and does not yet claim a completed perturbative spectral
density or double-Borel sum rule for the tensor current.
\end{abstract}

\tableofcontents

\section{Purpose and executable files}

The interactive source of this calculation is
\begin{center}
  \texttt{notebooks/DsBs\_gamma\_symbolic\_derivation.nb}.
\end{center}
It contains 38 input cells designed to be evaluated from top to bottom or one
at a time.  The noninteractive regression scripts are
\begin{align*}
  &\texttt{scripts/mathematica\_current\_wick\_trace\_audit.wl},\\
  &\texttt{scripts/mathematica\_correlator\_routing\_audit.wl},\\
  &\texttt{scripts/mathematica\_hard\_loop\_parameterization.wl},\\
  &\texttt{scripts/mathematica\_state\_mixing\_projection.wl}.
\end{align*}
The first three batch audits write their full machine-readable expressions
under \texttt{outputs/}; the state-mixing audit prints its exact residuals and
interval overlaps directly.  This note presents the compact analytic content
needed to understand and reproduce those expressions.

\section{Conventions and kinematics}

We use
\begin{equation}
  g_{\mu\nu}=\operatorname{diag}(1,-1,-1,-1),\qquad
  \{\gamma_\mu,\gamma_\nu\}=2g_{\mu\nu},
\end{equation}
\begin{equation}
  \sigma_{\mu\nu}=\frac{\ii}{2}[\gamma_\mu,\gamma_\nu],\qquad
  \epsilon^{0123}=+1.
\end{equation}
The \FeynCalc{} convention is explicitly checked through
\texttt{FeynCalc`\$LeviCivitaSign=-1}.

The momentum assignment is
\begin{equation}
  p^{\prime}=p+q,
\end{equation}
where $p^{\prime}$ is the initial $1^+$ momentum, $p$ is the final $0^-$
momentum, and
$q$ is the photon momentum.  The photon is real,
\begin{equation}
  q^2=0,\qquad 2p\cdot q=p^{\prime 2}-p^2.
\end{equation}
The heavy flavor is denoted by $Q=c,b$ and its mass by $m_Q$; the light flavor
is strange with mass $m_s$.

\section{Currents and the Rohrwild correlator}

The two basis-current vertices are
\begin{align}
  \Gamma^A_\mu
  &=\gamma_\mu\gamma_5,\\
  \Gamma^B_\mu
  &=\frac{\ii}{m_Q+m_s}\,
    \sigma_{\mu\alpha}p^{\prime\alpha}\gamma_5,
\end{align}
and the pseudoscalar vertex is
\begin{equation}
  \Gamma_P=\ii\gamma_5.
\end{equation}
The tensor vertex is independently represented as
\begin{equation}
  \Gamma^B_\mu
  =-\frac{(\gamma_\mu\slashedpp-\slashedpp\gamma_\mu)\gamma_5}
    {2(m_Q+m_s)}.
\end{equation}
\Mathematica{} verifies that the two definitions agree exactly.

The physical-current rotations are kept outside the basis traces:
\begin{align}
  \Gamma^{\rm low}_\mu
  &=\sin\theta\,\Gamma^A_\mu+\cos\theta\,\Gamma^B_\mu,\\
  \Gamma^{\rm high}_\mu
  &=\cos\theta\,\Gamma^A_\mu-\sin\theta\,\Gamma^B_\mu.
\end{align}

Following Rohrwild's vacuum three-point notation
\href{https://arxiv.org/abs/0708.1405}{arXiv:0708.1405}, adapted to a
$1^+\to0^-\gamma$ transition, the starting correlator is
\begin{equation}
  \Pi^X_{\mu\nu}(p,q)=\ii^2\int d^4x\,d^4y\,
  \ee^{\ii p\cdot x+\ii q\cdot y}
  \langle0|T\{J_P^\dagger(x)j_\nu^{\rm em}(y)J^X_\mu(0)\}|0\rangle,
  \qquad X=A,B,
  \label{eq:rohrwild-correlator}
\end{equation}
where
\begin{equation}
  j_\nu^{\rm em}=e_s\bar s\gamma_\nu s+e_Q\bar Q\gamma_\nu Q.
\end{equation}
Here $e_s,e_Q$ are charges in units of the positive elementary charge $e$.
Introduce the plane-wave background field
\begin{equation}
  F_{\alpha\beta}(z)=\ii
  (q_\alpha\varepsilon^*_\beta-q_\beta\varepsilon^*_\alpha)
  \ee^{\ii q\cdot z}.
\end{equation}
The term linear in this field obeys
\begin{equation}
  \varepsilon^{*\nu}\Pi^X_{\mu\nu}(p,q)
  =\ii\int d^4x\,\ee^{\ii p\cdot x}
  \langle0|T\{J_P^\dagger(x)J^X_\mu(0)\}|0\rangle_F
  \equiv
  \ii\int d^4x\,\ee^{\ii p\cdot x}
  \langle\gamma(q,\varepsilon)|T\{J_P^\dagger(x)J^X_\mu(0)\}|0\rangle,
  \label{eq:background-external-equivalence}
\end{equation}
up to the explicitly stated overall QED convention.  Thus the former
vacuum-to-photon formula was not a different calculation; it is the
single-photon component of Eq.~\eqref{eq:rohrwild-correlator}.

In explicit fields the ordered product is
\begin{equation}
  T\{\bar s(x)\Gamma_PQ(x)\,\bar Q(0)\Gamma^X_\mu s(0)\}.
  \label{eq:field-order}
\end{equation}
Thus the vertex at $x$ carries the final channel $p$, while the current at the
origin carries the initial channel $p^{\prime}=p+q$.

The current definitions used in the notebook are:
\begin{lstlisting}
gammaA[index_] := GA[index] . GA[5];
gammaB[index_] :=
  I FV[pPrime, alpha] DiracSigma[GA[index], GA[alpha]] . GA[5]/
    (mQ + ms);
gammaBExpanded[index_] :=
  -(GA[index] . GS[pPrime] - GS[pPrime] . GA[index]) . GA[5]/
    (2 (mQ + ms));
gammaP[] := I GA[5];
propNumerator[momentum_, mass_] := GS[momentum] + mass;
\end{lstlisting}

\section{Wick contraction and global signs}

For the complete hard contraction, Eq.~\eqref{eq:field-order} gives
\begin{equation}
  \langle T\{\bar s\Gamma_PQ\,\bar Q\Gamma_Xs\}\rangle
  =-\Tr_D[\Gamma_PS_Q\Gamma_XS_s].
\end{equation}
The minus sign is the closed-fermion-loop sign.  Including the leading
correlator factor $\ii$, but not yet the propagator or QED-vertex factors, the
hard prefactor is therefore
\begin{equation}
  -\ii N_c.
\end{equation}

If only the heavy flavor is contracted, the strange bilocal remains open and
there is no closed fermion loop.  The soft contraction begins with $+\ii$.
The Fierz rearrangement
\begin{equation}
  \bar s_\alpha(x)s_\beta(0)
  =-\frac14\sum_i(\Gamma_i)_{\beta\alpha}
  \bar s(x)\Gamma_i s(0)
\end{equation}
then gives a soft prefactor $-\ii/4$ before the free-propagator factor.

In the notebook the bookkeeping is kept visible:
\begin{lstlisting}
fermionLoopSign = -1;
hardWickPrefactor = I fermionLoopSign Nc;
softWickPrefactorBeforeFierz = I;
softWickPrefactorAfterFierz = -I/4;
\end{lstlisting}

\section{Propagator expansion and OPE building blocks}

The free momentum-space propagator is
\begin{equation}
  S_f^0(r)=\frac{\ii(\not\!r+m_f)}{r^2-m_f^2+\ii0}.
  \label{eq:free-propagator}
\end{equation}

\subsection{Light-strange propagator in Rohrwild notation, including $m_s$}

To make the comparison with Rohrwild direct, write $\bar u=1-u$ and keep the
background fields at the point $ux$.  With color indices displayed, the
light-strange propagator used as the master expansion is
\begin{align}
  \widehat{s^a(x)\bar s^b(0)}={}&
  \delta^{ab}\Bigg[
    \frac{\ii\not\!x}{2\pi^2x^4}
    -\frac{m_s}{4\pi^2x^2}
  \Bigg]
  \nonumber\\
  &-\frac{\ii g_s}{16\pi^2x^2}\int_0^1du\,
  \left\{\bar u\not\!x\sigma_{\alpha\beta}
  +u\sigma_{\alpha\beta}\not\!x\right\}
  G_A^{\alpha\beta}(ux)t^A_{ab}
  \nonumber\\
  &-\frac{\ii e_s\delta^{ab}}{16\pi^2x^2}\int_0^1du\,
  \left\{\bar u\not\!x\sigma_{\alpha\beta}
  +u\sigma_{\alpha\beta}\not\!x\right\}
  F^{\alpha\beta}(ux)
  \nonumber\\
  &-\frac{m_s}{32\pi^2}\int_0^1du\,
  \left[g_sG_A^{\alpha\beta}(ux)t^A_{ab}
       +e_s\delta^{ab}F^{\alpha\beta}(ux)\right]
  \sigma_{\alpha\beta}L_x+\cdots ,
  \label{eq:light-full-propagator}
\end{align}
where
\begin{equation}
  L_x=\ln\!\left(\frac{-x^2\mu^2}{4}\right)+2\gamma_E .
\end{equation}
The first line contains only the free propagator and its explicit $m_s$ term.
The last line is the linear-$m_s$ Wilson coefficient in a single gluon or
electromagnetic background field.  No local vacuum-condensate term is written
in Eq.~\eqref{eq:light-full-propagator}.  Setting $m_s$ and the last line to
zero gives precisely the light-propagator form displayed in Eq.~(2.12) of
Rohrwild.  The ellipsis denotes higher-background-field and higher-order mass
terms, not local condensate pieces used elsewhere.

\paragraph{Important calculation warning.}
Although local parts are no longer displayed as part of the propagator, the
existing axial numerical sum-rule implementation \emph{does include} the
term labeled \texttt{heavy\_local} in the Python audit.  After the double
Borel transform it is
\begin{equation}
  \Pi^{A,\mathrm{local}}_{Q\gamma}
  =e_Q\,\ee^{-m_Q^2/M^2}\langle\bar ss\rangle
  \left[
    1-\frac{m_Qm_s}{M^2}
    +\frac{m_s^2}{2M^2}\left(1+\frac{m_Q^2}{M^2}\right)
  \right].
  \label{eq:heavy-local}
\end{equation}
It has not been removed here, because doing so would change the quoted form
factors and widths.  The mixed condensate
$\langle\bar s g_s\sigma\cdot Gs\rangle$ and the vacuum gluon condensate were
not included in the radiative three-point calculation.

\subsection{Heavy propagator in a background gluon field}

For reference, the momentum representation through one background gluon can
be organized as
\begin{align}
  S_Q^{ab}(x)
  =\ii\int\frac{d^4k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}
  \Bigg\{&
  \frac{\delta^{ab}(\not\!k+m_Q)}{k^2-m_Q^2}
  -\frac{g_sG^A_{\alpha\beta}t^A_{ab}}{4}
  \frac{
    \sigma^{\alpha\beta}(\not\!k+m_Q)
    +(\not\!k+m_Q)\sigma^{\alpha\beta}}
  {(k^2-m_Q^2)^2}
  +\cdots\Bigg\}.
  \label{eq:heavy-full-propagator}
\end{align}
For the photon-DA calculation the one-gluon term is used as an operator
insertion, rather than replaced by $\langle G^2\rangle$.  The explicit
light-cone form used in the symbolic three-particle kernels is
\begin{align}
  S_Q^G(x)
  =-\ii g_s\int\frac{d^4k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}
  \int_0^1du\Bigg[
  &\frac{\not\!k+m_Q}{2(m_Q^2-k^2)^2}
    G^{\alpha\beta}(ux)\sigma_{\alpha\beta}
  \nonumber\\
  &+\frac{ux_\alpha}{m_Q^2-k^2}
    G^{\alpha\beta}(ux)\gamma_\beta
  \Bigg].
  \label{eq:gluon-background-propagator}
\end{align}
Both the $\sigma_{\alpha\beta}$ part and the
$x_\alpha\gamma_\beta$ part have Mathematica trace-kernel scripts.

\subsection{Electromagnetic background-field propagator}

The first-order electromagnetic correction is
\begin{align}
  S_f^\gamma(x)
  =-\ii e_f\int\frac{d^4k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}
  \int_0^1du\Bigg[
  &\frac{\not\!k+m_f}{2(m_f^2-k^2)^2}
    F^{\alpha\beta}(ux)\sigma_{\alpha\beta}
  \nonumber\\
  &+\frac{ux_\alpha}{m_f^2-k^2}
    F^{\alpha\beta}(ux)\gamma_\beta
  \Bigg].
  \label{eq:em-background-propagator}
\end{align}
The overall electromagnetic coupling may either be included in $e_f$ or kept
outside the propagator, but not both.  In the explicit-vertex trace audit,
Eq.~\eqref{eq:em-background-propagator} is represented equivalently by
\begin{equation}
  S_f^0(r)(-\ii e e_f\gamma_\nu\varepsilon^\nu)S_f^0(r+q),
\end{equation}
with the orientation fixed separately for each diagram.  These are alternative
representations of the same hard photon-emission term.

\subsection{Photon-DA matrix elements}

The condensate-dependent photon terms are vacuum-to-photon nonlocal matrix
elements.  For example,
\begin{align}
  \langle\gamma(q,\varepsilon)|\bar s(x)\sigma_{\mu\nu}s(0)|0\rangle
  ={}&-\ii e e_s\langle\bar ss\rangle
  (\varepsilon_\mu q_\nu-\varepsilon_\nu q_\mu)
  \int_0^1du\,\ee^{\ii\bar u q\cdot x}
  \left[\chi\phi_\gamma(u)+\frac{x^2}{16}\mathbb A(u)\right]
  \nonumber\\
  &+\text{the twist-4 }h_\gamma\text{ structure},
  \label{eq:tensor-photon-da}
\end{align}
and
\begin{equation}
  \langle\gamma(q,\varepsilon)|\bar s(x)\gamma_\mu s(0)|0\rangle
  =e e_s f_{3\gamma}\widetilde\varepsilon_\mu
  \int_0^1du\,\ee^{\ii\bar u q\cdot x}\psi^v(u).
  \label{eq:vector-photon-da}
\end{equation}
The three-particle matrix elements
$\langle\gamma|\bar s(x)g_sG_{\alpha\beta}(vx)\Gamma s(0)|0\rangle$
define $\mathcal S,\widetilde{\mathcal S},\mathcal T_1,\ldots,\mathcal T_4$.
Their axial combination used in the sum rule is
\begin{equation}
  \mathcal F_1=
  \mathcal S+\widetilde{\mathcal S}-\mathcal T_1-\mathcal T_2
  +\mathcal T_3+\mathcal T_4
  +2v(-\mathcal S-\mathcal T_3+\mathcal T_2).
  \label{eq:F1-combination}
\end{equation}

\section{Momentum routing}

\subsection{Heavy-line emission}

The three fermion momenta are $k$, $k+q$, and $k-p$.  The denominators are
\begin{align}
  d_{H1}&=(k+q)^2-m_Q^2,\\
  d_{H2}&=k^2-m_Q^2,\\
  d_{H3}&=(k-p)^2-m_s^2.
\end{align}
The current momenta are
\begin{equation}
  k-(k-p)=p,\qquad (k+q)-(k-p)=p+q.
\end{equation}

\subsection{Strange-line emission}

The three momenta are $k$, $k-p$, and $k-p-q$.  The denominators are
\begin{align}
  d_{S1}&=k^2-m_Q^2,\\
  d_{S2}&=(k-p)^2-m_s^2,\\
  d_{S3}&=(k-p-q)^2-m_s^2.
\end{align}
The corresponding current momenta are
\begin{equation}
  k-(k-p)=p,\qquad k-(k-p-q)=p+q.
\end{equation}

This vertex check is important.  The old trial route $k-p+q$ gives
$k-(k-p+q)=p-q$ at the initial vertex and is therefore not the routing of
Eq.~\eqref{eq:rohrwild-correlator}.  It is kept only in the dedicated routing
audit as a diagnostic comparison.

\section{Hard-emission Dirac traces}

Charges, color, denominators, the QED vertex, propagator factors, and the
global Wick sign are deliberately kept outside the numerator traces.  For a
generic basis vertex $\Gamma^X_\mu$, the heavy-emission numerator is
\begin{equation}
  N^X_{H,\mu\nu}=\Tr_D\!\left[
  \ii\gamma_5(\slashedk+m_Q)\gamma_\nu
  (\slashedk+\slashedq+m_Q)\Gamma^X_\mu
  (\slashedk-\slashedp+m_s)\right].
  \label{eq:heavy-trace}
\end{equation}
The strange-emission numerator is
\begin{equation}
  N^X_{s,\mu\nu}=\Tr_D\!\left[
  \ii\gamma_5(\slashedk+m_Q)\Gamma^X_\mu
  (\slashedk-\slashedp-\slashedq+m_s)\gamma_\nu
  (\slashedk-\slashedp+m_s)\right].
  \label{eq:strange-trace}
\end{equation}

The implementation is short enough to display in full:
\begin{lstlisting}
traceReduce[expression_] :=
  Collect2[
    DiracSimplify[expression, DiracSubstitute67 -> True],
    {mQ, ms}
  ];

heavyTrace[current_] := traceReduce[DiracTrace[
  gammaP[] . propNumerator[k, mQ] . GA[nu] .
  propNumerator[k + q, mQ] . current[mu] .
  propNumerator[k - p, ms]
]];

strangeTrace[current_] := traceReduce[DiracTrace[
  gammaP[] . propNumerator[k, mQ] . current[mu] .
  propNumerator[k - p - q, ms] . GA[nu] .
  propNumerator[k - p, ms]
]];

nAHeavy   = heavyTrace[gammaA];
nAStrange = strangeTrace[gammaA];
nBHeavy   = heavyTrace[gammaB];
nBStrange = strangeTrace[gammaB];
\end{lstlisting}
Each of the four traces is recomputed after a cyclic rotation of the matrix
chain.  All four cyclic differences vanish exactly.

\section{Fermion-line Ward identities}

For equal masses on the photon-emitting segment and $B=A+q$,
\begin{equation}
  (\not\!A+m)\not\!q(\not\!B+m)
  =D_B(\not\!A+m)-D_A(\not\!B+m),
  \label{eq:ward-line}
\end{equation}
where $D_A=A^2-m^2$ and $D_B=B^2-m^2$.  Equation~\eqref{eq:ward-line}
shows explicitly that replacing the photon vertex by $q_\nu$ collapses one of
the adjacent propagators, as required by the Ward--Takahashi identity.

The notebook checks Eq.~\eqref{eq:ward-line} independently for the heavy line,
with $A=k$ and $B=k+q$, and the strange line, with $A=l-q$ and $B=l$:
\begin{lstlisting}
wardHeavyResidual = FCE[DiracSimplify[
  DiracGammaExpand[
    propNumerator[k, mQ] . GS[q] . propNumerator[k + q, mQ]
    - (SP[k + q, k + q] - mQ^2) propNumerator[k, mQ]
    + (SP[k, k] - mQ^2) propNumerator[k + q, mQ]
  ],
  DiracSubstitute67 -> True, DiracOrder -> True
]] // ScalarProductExpand // Simplify;
\end{lstlisting}
Both the heavy and strange residuals are zero.

\section{E1 projection}

The transverse E1 tensor is chosen as
\begin{equation}
  S_{\mu\nu}=p_\nu q_\mu-(p\cdot q)g_{\mu\nu}.
\end{equation}
For $q^2=0$,
\begin{equation}
  q^\nu S_{\mu\nu}=0.
\end{equation}
The normalized projector is
\begin{equation}
  \mathcal P_{E1}^{\mu\nu}
  =\frac{p^\nu q^\mu-(p\cdot q)g^{\mu\nu}}
  {2(p\cdot q)^2},
\end{equation}
and satisfies
\begin{equation}
  \mathcal P_{E1}^{\mu\nu}S_{\mu\nu}=1.
\end{equation}
The code is
\begin{lstlisting}
e1Tensor = FV[p, nu] FV[q, mu] - SP[p, q] MT[mu, nu];
e1Projector = e1Tensor/(2 SP[p, q]^2);

e1Project[expression_] := Collect2[
  ScalarProductExpand[
    Contract[expression e1Projector] /. kinematicRules
  ],
  {mQ, ms}
];

projAHeavy   = e1Project[nAHeavy];
projAStrange = e1Project[nAStrange];
projBHeavy   = e1Project[nBHeavy];
projBStrange = e1Project[nBStrange];
\end{lstlisting}
The projector normalization, photon Ward contraction, and contraction with a
physical initial-state polarization are all checked symbolically.

\section{Physical-state projection and the Colangelo limit}

\subsection{Rotation of the projected invariant amplitudes}

Let $\widehat T_A$ and $\widehat T_B$ denote the continuum-subtracted,
double-Borel E1 invariant amplitudes obtained from the two basis currents.
Because the correlator is linear in the current at the initial-state vertex,
the physical projections are
\begin{equation}
  \begin{pmatrix}\widehat T_1\\[2pt]\widehat T_2\end{pmatrix}
  =R(\theta)
  \begin{pmatrix}\widehat T_A\\[2pt]\widehat T_B\end{pmatrix},
  \qquad
  R(\theta)=
  \begin{pmatrix}
    \sin\theta&\cos\theta\\
    \cos\theta&-\sin\theta
  \end{pmatrix},
  \qquad R^TR=\mathbf 1.
  \label{eq:state-rotation}
\end{equation}
The same rotation therefore applies after the E1 projection, after the OPE,
and after the Borel transformation; these linear operations commute.

Define the pseudoscalar and physical axial-state residues by
\begin{align}
  \langle0|J_P|P(p)\rangle
  &=\frac{f_Pm_P^2}{m_Q+m_s},
  \label{eq:pseudoscalar-residue}\\
  \langle0|J_i^\mu|H_i(p^{\prime},\eta)\rangle
  &=f_iM_i\eta^\mu,
  \qquad i=1,2,
  \label{eq:physical-decay-constant-definition}
\end{align}
and use
\begin{equation}
  \langle\gamma(q,\varepsilon)P(p)|H_i(p^{\prime},\eta)\rangle
  =eG_i\big[(\varepsilon^*\!\cdot\eta)(p\cdot q)
  -(\varepsilon^*\!\cdot p)(\eta\cdot q)\big].
  \label{eq:mixed-transition-amplitude}
\end{equation}
The pole term in the projected, double-Borel invariant is then
\begin{equation}
  \widehat T_i^{\rm pole}
  =\frac{f_Pm_P^2}{m_Q+m_s}\,f_iM_iG_i
  \exp\!\left(-\frac{M_i^2}{\mathcal M_1^2}
               -\frac{m_P^2}{\mathcal M_2^2}\right).
  \label{eq:mixed-hadronic-pole}
\end{equation}
Consequently the correctly normalized physical coupling is
\begin{equation}
  G_i=
  \frac{m_Q+m_s}{f_Pm_P^2f_iM_i}
  \exp\!\left(\frac{M_i^2}{\mathcal M_1^2}
              +\frac{m_P^2}{\mathcal M_2^2}\right)
  \widehat T_i^{\rm OPE}.
  \label{eq:mixed-coupling-from-ope}
\end{equation}
If the basis residues for a given pole are defined with the same mass
normalization, Eq.~\eqref{eq:mixed-coupling-from-ope} becomes
\begin{align}
  G_1
  &=\frac{\sin\theta\,f_A^{(1)}G_A^{(1)}
          +\cos\theta\,f_B^{(1)}G_B^{(1)}}{f_1},
  \label{eq:residue-weighted-low}\\
  G_2
  &=\frac{\cos\theta\,f_A^{(2)}G_A^{(2)}
          -\sin\theta\,f_B^{(2)}G_B^{(2)}}{f_2}.
  \label{eq:residue-weighted-high}
\end{align}
Thus a bare sine--cosine rotation of already normalized couplings is valid
only when the corresponding residues cancel.

\subsection{Colangelo-style final sum-rule assembly}

For the paper we organize the answer at the level of the projected Borel
invariants, rather than displaying the unprojected correlation function.  In
the equal-Borel convention
$\mathcal M_1^2=\mathcal M_2^2=2M^2$, define
\begin{equation}
  \mathcal N_i(M^2)=
  \frac{\exp[(M_i^2+m_P^2)/(2M^2)](m_Q+m_s)}
  {M_if_i\,m_P^2f_P},
  \qquad i=1,2.
  \label{eq:physical-normalization-factor}
\end{equation}
The two physical couplings are then presented directly as
\begin{align}
  G_1
  &=\mathcal N_1
    \left(\sin\theta\,\widehat T_A
          +\cos\theta\,\widehat T_B\right),
  \label{eq:paper-final-g1}\\
  G_2
  &=\mathcal N_2
    \left(\cos\theta\,\widehat T_A
          -\sin\theta\,\widehat T_B\right).
  \label{eq:paper-final-g2}
\end{align}
Each basis invariant is decomposed into the same OPE classes,
\begin{equation}
  \widehat T_X=
  \widehat T_X^{\rm pert}
  +\widehat T_X^{\langle\bar ss\rangle}
  +\widehat T_X^{\rm tw2}
  +\widehat T_X^{\rm tw3}
  +\widehat T_X^{\rm tw4}
  +\widehat T_X^{\rm 3p},
  \qquad X=A,B.
  \label{eq:basis-ope-decomposition}
\end{equation}

For the axial current, the Colangelo-style comparison invariant within the
adopted truncation is
\begin{align}
  \widehat T_A={}&
  \int_{(m_Q+m_s)^2}^{s_0}ds\,
  \ee^{-s/M^2}\rho_A^P(s)
  \nonumber\\
  &+e_QE_Q\langle\bar ss\rangle
  \left[
    1-\frac{m_Qm_s}{M^2}
    +\frac{m_s^2}{2M^2}
     \left(1+\frac{m_Q^2}{M^2}\right)
  \right]
  \nonumber\\
  &-e_s\langle\bar ss\rangle(E_Q-E_0)M^2
    \chi_{\rm C}\phi_\gamma(u_0)
  \nonumber\\
  &-e_s\langle\bar ss\rangle E_Q
  \left[
    -\frac14\bigl(\mathbb A(u_0)-8\bar H_\gamma(u_0)\bigr)
      \left(1+\frac{m_Q^2}{M^2}\right)
    -\mathcal I_{\mathcal F_1}(u_0)
  \right]
  \nonumber\\
  &+2e_sf_{3\gamma}m_QE_Q\Psi^v(u_0),
  \label{eq:full-axial-borel-invariant}
\end{align}
where
\begin{equation}
  E_Q=\ee^{-m_Q^2/M^2},
  \qquad E_0=\ee^{-s_0/M^2},
  \label{eq:borel-exponent-shorthand}
\end{equation}
\begin{align}
  \bar H_\gamma(u_0)
  &=\int_0^{u_0}du\int_0^u dv\,h_\gamma(v),\\
  \Psi^v(u_0)
  &=\int_0^{u_0}du\,\psi^v(u),
\end{align}
and the three-particle contribution is
\begin{align}
  \mathcal I_{\mathcal F_1}(u_0)={}&
  \int_0^{1-u_0}dv
  \int_0^{u_0/(1-v)}d\alpha_g\,
  \mathcal F_1\bigl(u_0-(1-v)\alpha_g,
                    1-u_0-v\alpha_g,\alpha_g\bigr)
  \nonumber\\
  &+\int_{1-u_0}^{1}dv
  \int_0^{(1-u_0)/v}d\alpha_g\,
  \mathcal F_1\bigl(u_0-(1-v)\alpha_g,
                    1-u_0-v\alpha_g,\alpha_g\bigr).
  \label{eq:F1-integral-compact}
\end{align}
Here $\chi_{\rm C}$ is the signed susceptibility convention printed by
Colangelo et al.  The project stores the positive magnitude
$\chi_\gamma=|\chi_{\rm C}|$, so the twist-2 term is implemented with the
equivalent replacement
\begin{equation}
  -e_s\langle\bar ss\rangle\chi_{\rm C}
  \longrightarrow
  +e_s\langle\bar ss\rangle\chi_\gamma.
  \label{eq:chi-convention-conversion}
\end{equation}

\subsection{Paper default: Rohrwild nonlocal transition OPE}

The standalone local term in Eq.~\eqref{eq:full-axial-borel-invariant} is
\emph{not} part of the paper-default transition sum rule.  Denote by
$\widehat T_A^{\rm base}$ the right-hand side of that equation with the
$e_Q\langle\bar ss\rangle$ local term removed.  The two schemes used in the
numerical comparison are
\begin{align}
  \widehat T_A^{\rm Col}
  &=\widehat T_A^{\rm base}
    +e_QE_Q\langle\bar ss\rangle
      \left[1-\frac{m_Qm_s}{M^2}
      +\frac{m_s^2}{2M^2}\left(1+\frac{m_Q^2}{M^2}\right)\right],
  \label{eq:colangelo-local-alternative}\\
  \widehat T_A^{\rm RW}
  &=\widehat T_A^{\rm base}+\mathcal I_A^{\rm em},
  \label{eq:rohrwild-nonlocal-default}
\end{align}
and they are alternatives: the two last terms must never be added.

At the symmetric double-Borel point $u_0=1/2$, the current-specific axial
trace gives $(1-2u)\mathcal S_\gamma-\mathcal T_4^\gamma$ for the direct
part.  Both direct integrals vanish by antisymmetry, leaving
\begin{equation}
  \mathcal I_A^{\rm em}
  =e_Q\langle\bar ss\rangle(E_Q-E_0)
   \frac{2(m_P^2-m_A^2)}{M^2}\,P_\gamma,
  \qquad
  P_\gamma=\ln 8-\frac{1181}{320}=-1.611183458320\ldots .
  \label{eq:axial-rohrwild-em-final}
\end{equation}
The source convention used here is
\begin{align}
 \mathcal S_\gamma
 &=60\alpha_g^2(\alpha_q+\alpha_{\bar q})
     [4-7(\alpha_q+\alpha_{\bar q})],\\
 \mathcal T_4^\gamma
 &=60\alpha_g^2(\alpha_{\bar q}-\alpha_q)
     [4-7(\alpha_q+\alpha_{\bar q})].
\end{align}
The third integral in the printed appendix representation of
$\mathcal P[\mathcal T_4^\gamma]$ has lower limit zero and is logarithmically
divergent if read literally.  Enforcing the double-Borel support
$\alpha_{\bar q}\geq1/2$ gives the finite constant $P_\gamma$ above.  This
support qualification is retained explicitly in the Python output rather
than silently absorbed into a numerical coefficient.

For the tensor basis current, with the stated physical-residue numerator
prescription
\begin{equation}
 p^2=m_P^2,\qquad p\cdot q=\frac{m_A^2-m_P^2}{2},\qquad u_0=\frac12,
\end{equation}
the corresponding nonlocal electromagnetic term is
\begin{align}
 \mathcal I_B^{\rm em}
 ={}&e_Q\langle\bar ss\rangle(E_Q-E_0)
 \left[(r_0-r_S)\frac{25}{16}-r_T\frac{5}{16}
 +2r_0\frac{m_P^2-m_A^2}{M^2}P_\gamma\right],
 \label{eq:tensor-rohrwild-em-final}\\
 r_0={}&\frac{m_Q}{m_Q+m_s},\qquad
 r_S=\frac{m_Q^2+\tfrac12 p\cdot q}{m_Q(m_Q+m_s)},\qquad
 r_T=\frac{-m_Q^2+m_P^2+\tfrac32 p\cdot q}{m_Q(m_Q+m_s)}.
\end{align}
Equations~\eqref{eq:axial-rohrwild-em-final} and
\eqref{eq:tensor-rohrwild-em-final} are implemented in
\texttt{scripts/rohrwild\_em\_da.py}.

\begin{table}[H]
 \centering
 \small
 \begin{tabular}{p{0.34\textwidth}p{0.25\textwidth}p{0.25\textwidth}}
  \toprule
  Contribution & Rohrwild paper default & Colangelo comparison\\
  \midrule
  Ordinary local condensate in transition LCSR & absent & retained for $J_A$\\
  $\mathcal S_\gamma,\mathcal T_4^\gamma$ & included nonlocally & not added separately\\
  Gluonic photon DAs & included & included through $\mathcal F_1$\\
  Local condensates in two-point $f_i$ sum rules & required & required\\
  Local plus electromagnetic three-particle term & forbidden double counting & forbidden double counting\\
  \bottomrule
 \end{tabular}
 \caption{Separation of the local-condensate prescriptions.}
 \label{tab:local-scheme-comparison}
\end{table}

For clarity, the perturbative density is written without the ambiguous
``$s\leftrightarrow Q$'' shorthand.  Define
\begin{align}
  \rho_i(s;m_i,m_j,e_i)={}&
  -\frac{3e_i}{8\pi^2}
  \Bigg\{
  2m_i\ln\!\frac{
    s-m_j^2+m_i^2-\lambda^{1/2}(s,m_j^2,m_i^2)}{
    s-m_j^2+m_i^2+\lambda^{1/2}(s,m_j^2,m_i^2)}
  \nonumber\\
  &\hspace{4.5em}
  +(m_j-m_i)\frac{m_j^2-m_i^2-s}{s^2}
  \lambda^{1/2}(s,m_j^2,m_i^2)
  \Bigg\},
\end{align}
so that
\begin{equation}
  \rho_A^P(s)=
  \rho_s(s;m_s,m_Q,e_s)-\rho_Q(s;m_Q,m_s,e_Q).
  \label{eq:axial-perturbative-density}
\end{equation}

The tensor-current invariant is kept in the identical paper-ready
decomposition
\begin{equation}
  \widehat T_B=
  \widehat T_B^{\rm pert}
  +\widehat T_B^{\langle\bar ss\rangle}
  +\widehat T_B^{\rm tw2}
  +\widehat T_B^{\rm tw3}
  +\widehat T_B^{\rm tw4}
  +\widehat T_B^{\rm 3p}.
  \label{eq:tensor-ope-decomposition}
\end{equation}
The Python result now fills these slots using the diagonal double-dispersion
mapping for the perturbative term and the documented physical-residue
prescription for the tensor numerators.  The ordinary local-condensate slot is
zero by the Rohrwild scheme, while Eq.~\eqref{eq:tensor-rohrwild-em-final}
supplies the nonlocal electromagnetic contribution.  The next Mathematica
stage is an independent cell-by-cell duplication of these already fixed
Python prescriptions; it does not change Eqs.~\eqref{eq:paper-final-g1} and
\eqref{eq:paper-final-g2}.

\subsection{Exact pure-axial reduction to Colangelo et al.}

Colangelo, De Fazio, and Ozpineci use the single axial current
$J^A_\mu=\bar Q\gamma_\mu\gamma_5s$ in their correlator.  This is the
Hermitian-conjugate orientation of our $A$ current and has the same invariant
amplitude.  In the convention of Eq.~\eqref{eq:state-rotation}, their
$D_{s1}(2460)$ calculation is obtained from the low channel by choosing
\begin{equation}
  \boxed{\theta=\frac{\pi}{2}=90^\circ},
  \qquad J_1=J_A,\qquad J_2=-J_B.
  \label{eq:colangelo-angle}
\end{equation}
At this point
\begin{equation}
  \widehat T_1=\widehat T_A,\qquad f_1=f_A,\qquad G_1=G_A.
  \label{eq:pure-axial-identities}
\end{equation}
For the equal-Borel convention
$\mathcal M_1^2=\mathcal M_2^2=2M^2$,
Eq.~\eqref{eq:mixed-coupling-from-ope} reduces to
\begin{equation}
  \left.G_1\right|_{\theta=\pi/2}
  =\frac{\exp[(M_1^2+m_P^2)/(2M^2)](m_Q+m_s)}
  {M_1f_A\,m_P^2f_P}\,\widehat T_A^{\rm OPE}.
  \label{eq:colangelo-formula-limit}
\end{equation}
For $Q=c$, $P=D_s$, and $M_1=m_{D_{s1}}$, the right-hand side is exactly the
prefactor and axial OPE appearing in Eq.~(4.4) of
\href{https://arxiv.org/abs/hep-ph/0505195}{Colangelo, De Fazio, and
Ozpineci}.  Therefore the relation is analytic, not merely a numerical
similarity.  Choosing $\theta=0$ instead places the pure axial current in the
second row of Eq.~\eqref{eq:state-rotation}; it swaps the low/high labels and
is not our $D_{s1}(2460)$ convention.

The numerical pure-$A$ comparison is shown in
Table~\ref{tab:colangelo-projection-comparison}.
\begin{table}[H]
  \centering
  \small
  \begin{tabular}{lll}
    \toprule
    Calculation & $G\,[\mathrm{GeV}^{-1}]$ & $\Gamma\,[\mathrm{keV}]$\\
    \midrule
    Colangelo et al., single $J_A$
      & $-0.37$ to $-0.29$ & $19$ to $29$\\
    This project, Stage 2 at $\theta=90^\circ$
      & $-0.3978$ to $-0.3124$ & $20.51$ to $33.26$\\
    Interval overlap
      & $-0.3700$ to $-0.3124$ & $20.51$ to $29.00$\\
    \bottomrule
  \end{tabular}
  \caption{Pure-axial benchmark.  The remaining displacement is caused by the
  input set and convention choices, not by the state projector.}
  \label{tab:colangelo-projection-comparison}
\end{table}
No intermediate angle is fitted here.  Formally, at fixed residues,
$G_1(\theta)=a\sin\theta+b\cos\theta$ with
$a=f_A^{(1)}G_A^{(1)}/f_1$ and
$b=f_B^{(1)}G_B^{(1)}/f_1$.  A physical angle extraction requires the
complete tensor-current amplitude and the angle-dependent physical residue
$f_1(\theta)$; both are still incomplete.

\subsection{Decay constants from the rotated two-point correlator}

Introduce the transverse two-point matrix
\begin{equation}
  \Pi^{\rm basis}=
  \begin{pmatrix}\Pi_{AA}&\Pi_{AB}\\\Pi_{AB}&\Pi_{BB}\end{pmatrix}.
\end{equation}
The physical matrix is
$\Pi^{\rm phys}=R\Pi^{\rm basis}R^T$, so that
\begin{align}
  \Pi_{11}
  &=\sin^2\theta\,\Pi_{AA}+\cos^2\theta\,\Pi_{BB}
    +2\sin\theta\cos\theta\,\Pi_{AB},
  \label{eq:pi11-mixed}\\
  \Pi_{22}
  &=\cos^2\theta\,\Pi_{AA}+\sin^2\theta\,\Pi_{BB}
    -2\sin\theta\cos\theta\,\Pi_{AB},
  \label{eq:pi22-mixed}\\
  \Pi_{12}
  &=\sin\theta\cos\theta(\Pi_{AA}-\Pi_{BB})
    +(\cos^2\theta-\sin^2\theta)\Pi_{AB}.
  \label{eq:pi12-mixed}
\end{align}
This is already the useful paper-level explicit form.  If each basis
correlator is decomposed as
\begin{equation}
  \widehat\Pi_{XY}=
  \int_{s_{\rm th}}^{s_0}ds\,\ee^{-s/\mathcal M^2}
  \rho_{XY}^{\rm pert}(s)
  +\sum_d\widehat\Pi_{XY}^{(d)},
  \qquad XY=AA,BB,AB,
  \label{eq:twopoint-basis-ope}
\end{equation}
then substitution gives, without an unreadably long expansion,
\begin{align}
  \widehat\Pi_{11}={}&
  \int_{s_{\rm th}}^{s_0}ds\,\ee^{-s/\mathcal M^2}
  \left[
    \sin^2\theta\,\rho_{AA}^{\rm pert}
    +\cos^2\theta\,\rho_{BB}^{\rm pert}
    +2\sin\theta\cos\theta\,\rho_{AB}^{\rm pert}
  \right]
  \nonumber\\
  &+\sum_d\left[
    \sin^2\theta\,\widehat\Pi_{AA}^{(d)}
    +\cos^2\theta\,\widehat\Pi_{BB}^{(d)}
    +2\sin\theta\cos\theta\,\widehat\Pi_{AB}^{(d)}
  \right],
  \label{eq:pi11-explicit-ope}\\
  \widehat\Pi_{22}={}&
  \int_{s_{\rm th}}^{s_0}ds\,\ee^{-s/\mathcal M^2}
  \left[
    \cos^2\theta\,\rho_{AA}^{\rm pert}
    +\sin^2\theta\,\rho_{BB}^{\rm pert}
    -2\sin\theta\cos\theta\,\rho_{AB}^{\rm pert}
  \right]
  \nonumber\\
  &+\sum_d\left[
    \cos^2\theta\,\widehat\Pi_{AA}^{(d)}
    +\sin^2\theta\,\widehat\Pi_{BB}^{(d)}
    -2\sin\theta\cos\theta\,\widehat\Pi_{AB}^{(d)}
  \right].
  \label{eq:pi22-explicit-ope}
\end{align}
Writing $\widehat\Pi_{ij}$ for the continuum-subtracted Borel invariants, the
direct decay-constant sum rules would be
\begin{align}
  f_1^2(\theta)
  &=\frac{\ee^{M_1^2/\mathcal M^2}}{M_1^2}
  \left[
    \sin^2\theta\,\widehat\Pi_{AA}
    +\cos^2\theta\,\widehat\Pi_{BB}
    +2\sin\theta\cos\theta\,\widehat\Pi_{AB}
  \right],
  \label{eq:f1-mixed-sumrule}\\
  f_2^2(\theta)
  &=\frac{\ee^{M_2^2/\mathcal M^2}}{M_2^2}
  \left[
    \cos^2\theta\,\widehat\Pi_{AA}
    +\sin^2\theta\,\widehat\Pi_{BB}
    -2\sin\theta\cos\theta\,\widehat\Pi_{AB}
  \right].
  \label{eq:f2-mixed-sumrule}
\end{align}
The condition $\widehat\Pi_{12}\simeq0$ can be used to diagnose or determine
the preferred mixing angle.  At $\theta=\pi/2$,
Eq.~\eqref{eq:f1-mixed-sumrule} becomes the pure axial-current result
\begin{equation}
  f_1^2=\frac{\ee^{M_1^2/\mathcal M^2}}{M_1^2}
  \widehat\Pi_{AA},
\end{equation}
which is the decay-constant normalization used by Colangelo et al.

The qualification ``would be'' is important: in this project only the
$AA$ OPE below is explicit.  A dedicated local calculation of
$\rho_{BB}$, $\rho_{AB}$ and their condensate terms has not yet been
completed.  Consequently Eqs.~\eqref{eq:pi11-explicit-ope} and
\eqref{eq:pi22-explicit-ope} are exact rotation formulae, but they are not yet
three fully evaluated two-point OPEs.

For completeness, their explicit axial two-point sum rule, generalized by
$m_c\to m_Q$, is
\begin{align}
  f_A^2={}&\frac{\ee^{M_A^2/\mathcal M^2}}{M_A^2}
  \Bigg\{
  \frac{1}{8\pi^2}
  \int_{(m_Q+m_s)^2}^{s_0}ds\,
  \lambda^{1/2}(s,m_Q^2,m_s^2)
  \nonumber\\
  &\quad\times
  \left[
    2-\frac{m_Q^2+m_s^2+6m_Qm_s}{s}
    -\frac{(m_Q^2-m_s^2)^2}{s^2}
  \right]\ee^{-s/\mathcal M^2}
  \nonumber\\
  &\quad+
  \ee^{-m_Q^2/\mathcal M^2}
  \left[
    \langle\bar ss\rangle
    \left(m_Q-\frac{m_Q^2m_s}{2\mathcal M^2}
    +\frac{m_Q^3m_s^2}{2\mathcal M^4}\right)
    -\frac{\langle\bar s\sigma_{\mu\nu}g_sG^{\mu\nu}s\rangle}{4}
    \frac{m_Q^3}{\mathcal M^4}
  \right]
  \Bigg\},
  \label{eq:colangelo-decay-constant-sumrule}
\end{align}
where
$\lambda(a,b,c)=a^2+b^2+c^2-2ab-2ac-2bc$.
Notice that the mixed condensate occurs here in the two-point decay-constant
sum rule even though it has not been included in our radiative three-point
sum rule.  For the charm channel the benchmark value is
$f_A\simeq0.225\,\mathrm{GeV}$.

\subsection{What was actually obtained for $f_1$ and $f_2$}

The numerical scripts used the reduced overlap model obtained after stripping
the common pole and Borel factors,
\begin{align}
  f_1^2&=\sin^2\theta f_A^2+\cos^2\theta f_B^2
  +2\sin\theta\cos\theta\,\rho_{AB}f_Af_B,
  \label{eq:f1-overlap-model}\\
  f_2^2&=\cos^2\theta f_A^2+\sin^2\theta f_B^2
  -2\sin\theta\cos\theta\,\rho_{AB}f_Af_B.
  \label{eq:f2-overlap-model}
\end{align}
For the $D_s$ sector the value $f_1=0.345(17)\,\mathrm{GeV}$ was used as a
working anchor, so that
\begin{equation}
  \rho_{AB}=
  \frac{f_1^2-\sin^2\theta f_A^2-\cos^2\theta f_B^2}
       {2\sin\theta\cos\theta f_Af_B},
  \label{eq:rho-from-f1-anchor}
\end{equation}
and Eq.~\eqref{eq:f2-overlap-model} then predicted $f_2$.  For the $B_s$
sector no $f_1$ anchor was available; instead the model imposed
$\Pi_{12}=0$, which gives
\begin{equation}
  \rho_{AB}^{\rm diag}=
  -\frac{\sin\theta\cos\theta(f_A^2-f_B^2)}
  {(\cos^2\theta-\sin^2\theta)f_Af_B}.
  \label{eq:rho-diagonal-closure}
\end{equation}
The saved central-angle scan summaries are
\begin{table}[H]
  \centering
  \small
  \begin{tabular}{llll}
    \toprule
    Sector and input & $f_1\,[\mathrm{GeV}]$ & $f_2\,[\mathrm{GeV}]$ & Status\\
    \midrule
    $D_s$, legacy $\chi_s$
      & $0.344\,[0.329,0.363]$ & $0.380\,[0.339,0.423]$
      & $f_1$ anchor; $f_2$ inferred\\
    $D_s$, lattice $f_{\gamma,s}^{\perp}$
      & $0.345\,[0.330,0.364]$ & $0.379\,[0.338,0.423]$
      & $f_1$ anchor; $f_2$ inferred\\
    $B_s(5830)$ closure, legacy $\chi_s$
      & $0.436\,[0.380,0.486]$ & $0.218\,[0.138,0.292]$
      & $\Pi_{12}=0$ model\\
    $B_s(5830)$ closure, lattice $f_{\gamma,s}^{\perp}$
      & $0.443\,[0.384,0.492]$ & $0.203\,[0.121,0.291]$
      & $\Pi_{12}=0$ model\\
    \bottomrule
  \end{tabular}
  \caption{Median and 16--84 percentile intervals at
  $\theta=35.3^\circ$.  These are the values found in the existing scans, but
  they are not independent predictions of a completed $AA/BB/AB$ two-point
  OPE calculation.}
  \label{tab:found-f1-f2}
\end{table}
For the paper, the safe presentation is therefore to show
Eqs.~\eqref{eq:pi11-mixed}--\eqref{eq:pi12-mixed}, quote the overlap-model
values with this qualification, and reserve the phrase ``QCD sum-rule
prediction of $f_1,f_2$'' for the future explicit $BB$ and $AB$ calculation.

Finally, once $G_i$ is normalized with the corresponding $f_i$, the decay
width is
\begin{equation}
  \Gamma(H_i\to P\gamma)
  =\frac{\alpha_{\rm em}}{3}|G_i|^2k_{\gamma,i}^3,
  \qquad
  k_{\gamma,i}=\frac{M_i^2-m_P^2}{2M_i}.
  \label{eq:mixed-radiative-width}
\end{equation}

\section{Inverse-denominator reduction}

The projected expressions contain $k^2$, $k\cdot p$, and $k\cdot q$.  For the
heavy-emission topology these are replaced by
\begin{align}
  k^2&=d_{H2}+m_Q^2,\\
  k\cdot q&=\frac{d_{H1}-d_{H2}}{2},\\
  k\cdot p&=\frac{d_{H2}+m_Q^2+p^2-m_s^2-d_{H3}}{2}.
\end{align}
For strange emission,
\begin{align}
  k^2&=d_{S1}+m_Q^2,\\
  k\cdot p&=\frac{d_{S1}+m_Q^2+p^2-m_s^2-d_{S2}}{2},\\
  k\cdot q&=p\cdot q+\frac{d_{S2}-d_{S3}}{2}.
\end{align}

Setting all three inverse denominators of a topology to zero extracts the
coefficient of the genuine three-denominator triangle.  Terms containing one
or more $d_i$ cancel propagators and are retained separately in the full
machine output.

The axial triangle cores are
\begin{align}
  N^{A,\mathrm{core}}_H
  &=4\ii m_Q+
    \frac{4\ii m_Q^3-4\ii m_Q^2m_s}{p\cdot q},\\
  N^{A,\mathrm{core}}_s
  &=-4\ii m_s+
    \frac{4\ii m_Qm_s^2-4\ii m_s^3}{p\cdot q}.
\end{align}
The tensor-current cores are
\begin{align}
  N^{B,\mathrm{core}}_H
  &=\frac{8\ii m_Q^2-4\ii m_Qm_s}{m_Q+m_s}
    +\frac{4\ii m_Q^2p^2}{(m_Q+m_s)(p\cdot q)},\\
  N^{B,\mathrm{core}}_s
  &=\frac{-4\ii m_Qm_s+8\ii m_s^2}{m_Q+m_s}
    +\frac{4\ii m_s^2p^2}{(m_Q+m_s)(p\cdot q)}.
\end{align}
These expressions refer only to the numerator traces of
Eqs.~\eqref{eq:heavy-trace}--\eqref{eq:strange-trace}; the charge, color,
propagator, QED-vertex, and global Wick factors must still be attached.

\section{Feynman parameterization of the hard triangles}

For three denominators,
\begin{equation}
  \frac{1}{D_1D_2D_3}
  =2\int_0^1dx\int_0^{1-x}dy\,
  \frac{1}{[xD_1+yD_2+(1-x-y)D_3]^3}.
  \label{eq:feynman-identity}
\end{equation}
Equivalently one may use $x+y+z=1$.

\subsection{Heavy emission}

Assign $x,y,z$ to $d_{H1},d_{H2},d_{H3}$.  Direct completion of the square
gives
\begin{equation}
  xd_{H1}+yd_{H2}+zd_{H3}
  =(k+xq-zp)^2-\Delta_H,
\end{equation}
where
\begin{equation}
  \boxed{\Delta_H=(x+y)m_Q^2+zm_s^2-xz p^{\prime2}-yzp^2.}
  \label{eq:deltaH}
\end{equation}

\subsection{Strange emission}

Assign $x,y,z$ to $d_{S1},d_{S2},d_{S3}$.  Then
\begin{equation}
  xd_{S1}+yd_{S2}+zd_{S3}
  =[k-yp-z(p+q)]^2-\Delta_s,
\end{equation}
with
\begin{equation}
  \boxed{\Delta_s=xm_Q^2+(y+z)m_s^2-xyp^2-xz p^{\prime2}.}
  \label{eq:deltaS}
\end{equation}

The independent pairwise-invariant formula
\begin{equation}
  \Delta=\sum_i x_i m_i^2
  -\sum_{i<j}x_ix_j(r_i-r_j)^2
\end{equation}
reproduces Eqs.~\eqref{eq:deltaH} and \eqref{eq:deltaS}.  The notebook checks
both the completed-square and pairwise forms:
\begin{lstlisting}
deltaH = (x + y) mQ^2 + z ms^2 - x z pPrime2 - y z p2;
shiftH = x q - z p;
heavyResidual = simplexReduce[
  x dH1 + y dH2 + z dH3
  - (SP[k + shiftH, k + shiftH] - deltaH)
];

deltaS = x mQ^2 + (y + z) ms^2 - x y p2 - x z pPrime2;
shiftS = -y p - z (p + q);
strangeResidual = simplexReduce[
  x dS1 + y dS2 + z dS3
  - (SP[k + shiftS, k + shiftS] - deltaS)
];
\end{lstlisting}
Both residuals vanish exactly.

\section{Soft two-particle Fierz traces}

After contracting the heavy quark and Fierz rearranging the strange bilocal,
the Dirac factor is
\begin{equation}
  T_i^X=\Tr_D[\Gamma_P(\slashedk+m_Q)\Gamma^X_\mu\Gamma_i].
\end{equation}
The notebook evaluates the standard scalar, pseudoscalar, vector, axial, and
tensor basis.  The nonzero results for the axial current are
\begin{align}
  T^A_{1}&=4\ii k_\mu,\\
  T^A_{\gamma_\rho}&=-4\ii m_Q g_{\mu\rho},\\
  T^A_{\sigma_{\rho\lambda}}
  &=4g_{\lambda\mu}k_\rho-4g_{\mu\rho}k_\lambda.
\end{align}
For the tensor current,
\begin{align}
  T^B_{\gamma_\rho}
  &=\frac{4\ii}{m_Q+m_s}
    [k_\mu p^{\prime}_\rho-g_{\mu\rho}(k\cdot p^{\prime})],\\
  T^B_{\gamma_\rho\gamma_5}
  &=-\frac{4}{m_Q+m_s}\epsilon_{\mu\rho k p^{\prime}},\\
  T^B_{\sigma_{\rho\lambda}}
  &=\frac{4m_Q}{m_Q+m_s}
    [g_{\lambda\mu}p^{\prime}_\rho-g_{\mu\rho}p^{\prime}_\lambda].
\end{align}
All omitted entries vanish.  Cyclically rotating the matrix chain gives the
same tensor- and vector-basis traces for both currents.

\clearpage
\section{Implemented OPE terms: exact status}

It is not correct to describe every term below as independently completed in
the new Mathematica restart.  The existing project contains a mixture of
published axial-benchmark terms, new exact symbolic traces, and tensor-current
estimates.  The present status is:

\begin{table}[H]
  \centering
  \small
  \begin{tabular}{p{0.27\textwidth}p{0.27\textwidth}p{0.32\textwidth}}
    \toprule
    OPE contribution & Axial current $A$ & Tensor current $B$\\
    \midrule
    Perturbative photon from $Q$ and $s$
      & Published spectral density implemented numerically; corrected traces
        independently reproduced
      & Corrected traces and triangle cores derived; diagonal
        double-dispersion spectral mapping implemented in Python\\
    Local $e_Q\langle\bar ss\rangle$ term
      & Excluded in the Rohrwild result; retained only in the Colangelo
        comparison with $m_s,m_s^2$ corrections
      & Excluded in the Rohrwild result; no Colangelo $J_B$ term invented\\
    Electromagnetic three-particle DAs,
      $\mathcal S_\gamma,\mathcal T_4^\gamma$
      & Included through Eq.~\eqref{eq:axial-rohrwild-em-final}
      & Included through Eq.~\eqref{eq:tensor-rohrwild-em-final} with the
        stated physical-residue numerator prescription\\
    Twist-2 two-particle DA,
      $\chi\langle\bar ss\rangle\phi_\gamma$
      & Included in the numerical axial benchmark
      & Tensor trace and numerical trace-ratio contribution included\\
    Twist-4 two-particle DAs,
      $\mathbb A$ and $h_\gamma$
      & Included in the axial benchmark
      & Included with the tensor trace ratio at the Borel saddle\\
    Twist-3 two-particle DA,
      $f_{3\gamma}\psi^v$
      & Included in the axial benchmark
      & Included with the physical-residue trace ratio (it vanishes at the
        symmetric point for the default antisymmetric $\psi^v$ integral)\\
    Three-particle photon DAs,
      $\mathcal S,\widetilde{\mathcal S},\mathcal T_{1\ldots4}$
      & Full published $\mathcal F_1$ integral implemented numerically
      & Local-$\sigma$ and $x_\alpha\gamma_\beta$ kernels included with the
        documented double-pole residue-matching prescription\\
    Mixed condensate
      $\langle\bar s g_s\sigma\cdot Gs\rangle$
      & Not included in the radiative three-point sum rule
      & Not included\\
    Vacuum gluon condensate $\langle G^2\rangle$
      & Not included in the radiative three-point sum rule
      & Not included\\
    \bottomrule
  \end{tabular}
  \caption{Term-by-term distinction between implemented results and incomplete
  parts of the independent derivation.}
  \label{tab:ope-status}
\end{table}

\section{Verification summary and present boundary}

\begin{table}[H]
  \centering
  \begin{tabular}{p{0.57\textwidth}cc}
    \toprule
    Check & Result & Exact tests\\
    \midrule
    Currents, Wick signs, traces, E1 cores, soft trace cyclicity
      & PASS & 19/19\\
    Standard vertex routing
      & PASS & 4/4 momenta\\
    Heavy- and strange-line Ward identities
      & PASS & 2/2\\
    Shifted and pairwise Feynman denominators
      & PASS & 4/4\\
    State rotation, OPE assembly, Colangelo limit, decay constant, and width
      & PASS & 14/14\\
    Sequential evaluation of the interactive notebook
      & PASS & 38/38 cells\\
    \bottomrule
  \end{tabular}
  \caption{Status of the independent Mathematica/FeynCalc restart.}
\end{table}

The $B_s$ channel uses the same symbolic expressions with $m_Q\to m_b$ and
the appropriate heavy-quark charge.  No second Dirac-trace derivation is
needed.

The calculation deliberately stops here.  The next independent tasks are:
\begin{enumerate}
  \item independently audit the separately implemented
    $e_Q\langle\bar ss\rangle$ contribution and decide whether it is retained
    in the final numerical convention;
  \item reproduce the axial two- and three-particle photon-DA terms from the
    explicit matrix elements rather than importing the final published sum
    rule;
  \item perform the shifted loop integrals based on
    Eqs.~\eqref{eq:deltaH}--\eqref{eq:deltaS};
  \item derive the double discontinuity or an equivalent double-dispersion
    representation;
  \item apply continuum subtraction and the double Borel transform;
  \item reproduce the published axial-current spectral density as a
    normalization and sign benchmark;
  \item only then derive and numerically implement the tensor-current hard
    spectral density.
\end{enumerate}
The earlier Python spectral-density candidate is not used as an input to this
restart and is not changed by the work documented here.

\appendix
\section{Reproduction commands}

From \texttt{papers/Ds\_Bs\_gamma/}, run
\begin{lstlisting}[language={},basicstyle=\ttfamily\scriptsize]
/Applications/Wolfram.app/Contents/MacOS/WolframKernel -noprompt \
  -script scripts/mathematica_current_wick_trace_audit.wl

/Applications/Wolfram.app/Contents/MacOS/WolframKernel -noprompt \
  -script scripts/mathematica_correlator_routing_audit.wl

/Applications/Wolfram.app/Contents/MacOS/WolframKernel -noprompt \
  -script scripts/mathematica_hard_loop_parameterization.wl

/Applications/Wolfram.app/Contents/MacOS/WolframKernel -noprompt \
  -script scripts/mathematica_state_mixing_projection.wl
\end{lstlisting}
To regenerate the notebook from its source cells, run
\begin{lstlisting}[language={},basicstyle=\ttfamily\scriptsize]
/Applications/Wolfram.app/Contents/MacOS/WolframKernel -noprompt \
  -script scripts/build_dsbs_symbolic_notebook.wl
\end{lstlisting}

\end{document}
