\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  citecolor=blue!60!black,
  urlcolor=blue!60!black
}

\newcommand{\Ds}{D_s}
\newcommand{\Dsone}{D_{s1}}
\newcommand{\GeV}{\mathrm{GeV}}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\ee}{\mathrm{e}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\slashp}[1]{#1\!\!\!/}
\newcommand{\qbar}{\bar q}
\newcommand{\sbar}{\bar s}
\newcommand{\vev}[1]{\left\langle #1 \right\rangle}

\title{Working Notes for $\Dsone \to \Ds \gamma$ in Light-Cone QCD Sum Rules}
\author{Ds gamma project}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
These notes are a living derivation for the light-cone QCD sum-rule
calculation of $\Dsone(2460)\to\Ds\gamma$ and
$\Dsone(2536)\to\Ds\gamma$.  The purpose is pedagogical as well as practical:
each step is written so that a master's student can follow the choices,
conventions, and algebra before the final paper-level formulas are assembled.
\end{abstract}

\section{Conventions}

We use the mostly-minus metric
\begin{equation}
  g_{\mu\nu}=\mathrm{diag}(+1,-1,-1,-1),
\end{equation}
and
\begin{equation}
  \{\gamma_\mu,\gamma_\nu\}=2g_{\mu\nu},\qquad
  \sigma_{\mu\nu}=\frac{\ii}{2}[\gamma_\mu,\gamma_\nu],
  \qquad
  \gamma_5=\ii\gamma^0\gamma^1\gamma^2\gamma^3 .
\end{equation}
The Levi-Civita convention is
\begin{equation}
  \epsilon^{0123}=+1,\qquad \epsilon_{0123}=-1,
\end{equation}
so that
\begin{equation}
  \Tr[\gamma_5\gamma_\mu\gamma_\nu\gamma_\alpha\gamma_\beta]
  =-4\ii\,\epsilon_{\mu\nu\alpha\beta}.
\end{equation}
Our Fourier convention for a propagator is
\begin{equation}
  S(x)=\int\frac{d^4 k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}\,\widetilde S(k).
\end{equation}

\section{Currents and Momentum Assignment}

The external momenta are
\begin{equation}
  P=p+q,
\end{equation}
where $P$ is the initial axial-meson momentum, $p$ is the final pseudoscalar
$\Ds$ momentum, and $q$ is the real-photon momentum.

The pseudoscalar interpolating current is
\begin{equation}
  J_{\Ds}(x)=\sbar(x)\,\ii\gamma_5\,Q(x).
\end{equation}
For the axial channel we use two independent currents,
\begin{align}
  J^{(0)}_{A\mu}(x)
  &= \sbar(x)\gamma_\mu\gamma_5 Q(x),\\
  J^{(0)}_{B\mu}(x)
  &= \frac{\ii}{m_Q+m_s}\,
     \sbar(x)\sigma_{\mu\alpha}P^\alpha\gamma_5 Q(x).
\end{align}
The tensor current contracts with $P^\alpha$, not $p^\alpha$, because it
interpolates the initial axial state.  The factor $1/(m_Q+m_s)$ restores the
same mass dimension as the axial-vector current.

\section{Correlation Function}

For a generic axial current $\Gamma_\mu\in\{\gamma_\mu\gamma_5,\,
\ii\sigma_{\mu\alpha}P^\alpha\gamma_5/(m_Q+m_s)\}$ we study
\begin{equation}
  \Pi_\mu(p,q)
  =
  \ii\int d^4x\,\ee^{\ii p\cdot x}
  \langle \gamma(q,\varepsilon)|
  T\{ \sbar(x)\Gamma_\mu Q(x)\,
       \bar Q(0)\ii\gamma_5 s(0)\}
  |0\rangle .
  \label{eq:correlator}
\end{equation}
The target Lorentz structure for the $1^+\to0^-\gamma$ transition is
\begin{equation}
  (\eta\cdot\varepsilon^*)(p\cdot q)
  -(\eta\cdot q)(p\cdot\varepsilon^*).
\end{equation}
On the correlator side we therefore project onto an equivalent transverse
structure built from the open axial index and the photon polarization.

\section{Wick Contraction and OPE Bookkeeping}

The OPE is separated into a hard-photon sector and a soft-photon sector:
\begin{equation}
  \Pi_\mu^{\mathrm{OPE}}
  =
  \Pi_\mu^{\mathrm{hard}}
  +
  \Pi_\mu^{\mathrm{soft}}.
\end{equation}
This split is important because the two terms describe different physics and
must not be double counted.

\subsection{Hard photon emission}

In the hard sector the photon is emitted perturbatively from either the heavy
quark or the strange quark.  After Wick contraction one obtains
\begin{equation}
  \Pi_\mu^{\mathrm{hard}}
  =
  \ii N_c\int d^4x\,\ee^{\ii p\cdot x}
  \Tr_D\!\left[
    \Gamma_\mu S_Q^\gamma(x)\,\ii\gamma_5\,S_s^0(-x)
    +
    \Gamma_\mu S_Q^0(x)\,\ii\gamma_5\,S_s^\gamma(-x)
  \right],
  \label{eq:hard-wick}
\end{equation}
where $N_c=3$ and $\Tr_D$ denotes the Dirac trace.  The free massive propagator is
\begin{equation}
  S_q^0(x)
  =
  \int\frac{d^4k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}
  \frac{\ii(\slashp{k}+m_q)}{k^2-m_q^2}.
\end{equation}
We keep explicit powers of $m_s$, including possible $m_s^2$ terms.

The first-order electromagnetic background-field correction for a generic quark
flavor $q$ is
\begin{align}
  S_q^\gamma(x)
  &=
  -\ii e_q
  \int\frac{d^4k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}
  \int_0^1du
  \Bigg[
    \frac{\slashp{k}+m_q}{2(m_q^2-k^2)^2}
    F^{\alpha\beta}(ux)\sigma_{\alpha\beta}
    +
    \frac{u x_\alpha}{m_q^2-k^2}
    F^{\alpha\beta}(ux)\gamma_\beta
  \Bigg].
  \label{eq:em-propagator}
\end{align}
In Eq.~\eqref{eq:hard-wick} this generic formula is used twice:
\begin{align}
  S_Q^\gamma(x)
  &= S_q^\gamma(x)\big|_{q\to Q,\;m_q\to m_Q,\;e_q\to e_Q},\\
  S_s^\gamma(x)
  &= S_q^\gamma(x)\big|_{q\to s,\;m_q\to m_s,\;e_q\to e_s}.
\end{align}
Thus the hard sector contains both heavy-line and strange-line electromagnetic
background-field insertions.
For a real photon we write
\begin{equation}
  F^{\alpha\beta}(ux)
  =
  \ii(\varepsilon^\alpha q^\beta-\varepsilon^\beta q^\alpha)
  \ee^{\ii u q\cdot x},
\end{equation}
with the overall phase kept consistent with the Fourier convention.

Equation~\eqref{eq:em-propagator} is not a vacuum-condensate correction.  It is
the quark propagator in an external electromagnetic field and is included in
the base analysis.  What we do not include in the base hard sector are the
ordinary SVZ-style condensate-expanded propagator terms such as
$\langle\bar s s\rangle$, $\langle\bar s g_s\sigma Gs\rangle$, or
$\langle G^2\rangle$ propagator corrections.

\subsection{Equivalent momentum-space vertex form}

For FeynCalc trace checks it is often simpler to use the equivalent explicit
photon-vertex representation.  With photon index $\nu$,
\begin{align}
  N_{Q,\mu\nu}
  &=
  \Tr_D\!\left[
    \Gamma_\mu
    (\slashp{k}+\slashp{q}+m_Q)
    \gamma_\nu
    (\slashp{k}+m_Q)
    \ii\gamma_5
    (\slashp{k}-\slashp{p}+m_s)
  \right],
  \\
  N_{s,\mu\nu}
  &=
  \Tr_D\!\left[
    \Gamma_\mu
    (\slashp{k}+m_Q)
    \ii\gamma_5
    (\slashp{k}-\slashp{p}+m_s)
    \gamma_\nu
    (\slashp{k}-\slashp{p}+\slashp{q}+m_s)
  \right].
\end{align}
These numerators are accompanied by the denominators
\begin{align}
  D_Q &=
  [(k+q)^2-m_Q^2][k^2-m_Q^2][(k-p)^2-m_s^2],\\
  D_s &=
  [k^2-m_Q^2][(k-p)^2-m_s^2][(k-p+q)^2-m_s^2].
\end{align}
The explicit-vertex form and the background-field form represent the same hard
emission physics.  We must not add both as independent contributions.

\subsection{Soft photon emission: two-particle photon DAs}

In the soft sector the photon is represented by its light-cone distribution
amplitudes.  Contracting only the heavy quark gives
\begin{equation}
  \Pi_\mu^{\mathrm{soft},2p}
  =
  \ii\int d^4x\,\ee^{\ii p\cdot x}
  [\Gamma_\mu S_Q^0(x)\ii\gamma_5]_{\alpha\beta}
  \langle\gamma(q,\varepsilon)|
  \sbar_\alpha(x)s_\beta(0)
  |0\rangle .
\end{equation}
Fierz rearrangement converts the open spinor indices to a basis of Dirac
bilinears,
\begin{equation}
  \sbar_\alpha(x)s_\beta(0)
  =
  -\frac14\sum_i(\Gamma_i)_{\beta\alpha}
  \sbar(x)\Gamma_i s(0),
\end{equation}
so that
\begin{equation}
  \Pi_\mu^{\mathrm{soft},2p}
  =
  -\frac{\ii}{4}
  \int d^4x\,\ee^{\ii p\cdot x}
  \sum_i
  \Tr_D[\Gamma_\mu S_Q^0(x)\ii\gamma_5\Gamma_i]\,
  \langle\gamma(q,\varepsilon)|
  \sbar(x)\Gamma_i s(0)
  |0\rangle .
\end{equation}
The photon matrix elements are then expressed in terms of two-particle photon
DAs.  Parameters such as $\chi\langle\bar s s\rangle$ enter here as part of the
photon wavefunction normalization; they are not condensate corrections to the
hard propagator.

\subsection{Soft photon emission: three-particle photon DAs}

To include three-particle photon DAs we must also allow one background gluon to
come from the heavy-quark propagator,
\begin{align}
  S_Q^G(x)
  &=
  -\ii g_s
  \int\frac{d^4k}{(2\pi)^4}\,\ee^{-\ii k\cdot x}
  \int_0^1du
  \Bigg[
    \frac{\slashp{k}+m_Q}{2(m_Q^2-k^2)^2}
    G^{\alpha\beta}(ux)\sigma_{\alpha\beta}
    +
    \frac{u x_\alpha}{m_Q^2-k^2}
    G^{\alpha\beta}(ux)\gamma_\beta
  \Bigg].
  \label{eq:gluon-propagator}
\end{align}
This term is not a gluon-condensate correction.  It is an operator insertion
that combines with photon matrix elements of the form
\begin{equation}
  \langle\gamma(q,\varepsilon)|
  \sbar(x)\Gamma_i g_sG_{\alpha\beta}(ux)s(0)
  |0\rangle ,
\end{equation}
which define the three-particle photon DAs.

\section{Staged Calculation Plan}

We proceed in two stages.

\paragraph{Stage 1.}
Include the hard photon emission terms and the two-particle photon DAs:
\begin{equation}
  \Pi_\mu^{\mathrm{Stage\ 1}}
  =
  \Pi_\mu^{\mathrm{hard}}
  +
  \Pi_\mu^{\mathrm{soft},2p}.
\end{equation}
This stage keeps all explicit $m_s$ terms and omits ordinary
condensate-expanded propagators.

\paragraph{Stage 2.}
Add the three-particle photon DA contributions generated by
$S_Q^G$ and the corresponding light-cone matrix elements:
\begin{equation}
  \Pi_\mu^{\mathrm{Stage\ 2}}
  =
  \Pi_\mu^{\mathrm{Stage\ 1}}
  +
  \Pi_\mu^{\mathrm{soft},3p}.
\end{equation}
This staging keeps the derivation auditable: first we verify the core hard and
two-particle DA structures, then we add the more involved background-gluon
terms.

\section{Current FeynCalc Artifacts}

The script \texttt{scripts/step2\_current\_building\_blocks.wl} checks the
basic Dirac conventions and defines the current vertices.  The script
\texttt{scripts/step2\_hard\_photon\_numerators.wl} computes numerator-level
hard-photon traces in the explicit photon-vertex representation.  These traces
are stored in \texttt{outputs/step2\_hard\_photon\_numerators.txt}.

\section{Stage 1 Axial-Current Numerical Baseline}

Before deriving the tensor-current sum rule, we implemented the known
single-axial-current result for
$D_{s1}(2460)\to D_s\gamma$ as a benchmark.  This is the coupling called
$g_1$ by Colangelo, De Fazio, and Ozpineci.  In our notation this is the
axial-current form factor $G_A$.

The Stage 1 version contains
\begin{equation}
  G_A^{\mathrm{Stage\ 1}}
  =
  G_A^{\mathrm{pert}}
  +
  G_A^{\chi\phi_\gamma}
  +
  G_A^{\mathbb A,\bar H_\gamma}
  +
  G_A^{f_{3\gamma}\Psi^v},
\end{equation}
where the three-particle DA integral usually denoted by ${\cal F}_1$ is omitted
until Stage 2.

The numerical script is
\begin{center}
  \texttt{scripts/stage1\_axial\_g1\_baseline.py}.
\end{center}
It writes the full Borel/threshold grid to
\begin{center}
  \texttt{outputs/stage1\_axial\_g1\_baseline.csv}.
\end{center}

\subsection{Magnetic-susceptibility sign convention}

The Colangelo paper prints $\chi=-(3.15\pm0.30)\,\mathrm{GeV}^{-2}$ in its
matrix-element convention.  In this project we store the BBK magnitude as
\begin{equation}
  \chi(1\,\mathrm{GeV})=+3.15\pm0.30\,\mathrm{GeV}^{-2}.
\end{equation}
Therefore the sign of the $\chi\phi_\gamma$ term in the implemented sum rule is
flipped relative to the literal printed formula.  This is a convention
translation, not a physical change.  A diagnostic run that inserts positive
$\chi$ into the printed negative-$\chi$ formula gives a much larger width and is
kept only as a warning check.

\subsection{Preliminary Stage 1 result}

Using the project inputs, $u_0=1/2$, $3\le M^2\le6\,\mathrm{GeV}^2$, and
$s_0=(2.50,2.55,2.60)^2\,\mathrm{GeV}^2$, the axial-current Stage 1 grid gives
\begin{equation}
  -0.399 \le G_A^{\mathrm{Stage\ 1}} \le -0.314\quad \mathrm{GeV}^{-1}.
\end{equation}
With
\begin{equation}
  \Gamma=\frac{\alpha_{\rm em}}{3}G^2|\vec q_\gamma|^3,
\end{equation}
this corresponds to
\begin{equation}
  20.8\,\mathrm{keV}
  \le
  \Gamma_A^{\mathrm{Stage\ 1}}[D_{s1}(2460)\to D_s\gamma]
  \le
  33.5\,\mathrm{keV}.
\end{equation}
This is not yet the physical mixed-state result.  It is the axial-current
baseline that will be combined with the tensor-current form factor after the
$J_B$ sum rule is derived.

\end{document}
