\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,booktabs}
\usepackage{slashed}
\usepackage{hyperref}

\newcommand{\Bc}{B_c}
\newcommand{\Bcst}{B_c^\ast}
\newcommand{\BcOne}{B_{c1}}
\newcommand{\eps}{\epsilon}
\newcommand{\Slash}[1]{\slashed{#1}}
\newcommand{\GeV}{\mathrm{GeV}}

\title{Symbolic Projection Notes for \texorpdfstring{\(\BcOne\to \Bc^{(\ast)}\gamma\)}{Bc1 to Bc gamma}}
\author{Working notes}
\date{\today}

\begin{document}
\maketitle

\section{Scope}

These notes collect the compact FeynCalc projection results for the heavy-heavy
channels
\[
\BcOne(6743)\to \Bc\gamma,\qquad
\BcOne(6743)\to \Bcst\gamma,\qquad
\BcOne(6750)\to \Bc\gamma,\qquad
\BcOne(6750)\to \Bcst\gamma .
\]
The calculation is structurally different from the \(D_s\) and \(B_s\)
light-cone sum rules.  In the \(B_c\) system both valence constituents are
heavy, so the leading radiative OPE is a hard-photon heavy-heavy calculation.
There is no light spectator line to be replaced by photon distribution
amplitudes, and no \(\chi_s\langle\bar s s\rangle\) type term.

\section{Currents and Propagators}

For \(B_c^+\sim c\bar b\), we use
\[
j_5=\bar b\,i\gamma_5 c,\qquad
j_\rho^V=\bar b\,\gamma_\rho c ,
\]
and the two axial basis currents
\[
J_\mu^A=\bar b\,\gamma_\mu\gamma_5 c,\qquad
J_\mu^B=\frac{i}{m_b+m_c}\,
\bar b\,\sigma_{\mu\alpha}P^\alpha\gamma_5 c,
\qquad P=p+q .
\]
The physical currents are
\[
J_{1\mu}=\sin\theta\,J_\mu^A+\cos\theta\,J_\mu^B,\qquad
J_{2\mu}=\cos\theta\,J_\mu^A-\sin\theta\,J_\mu^B .
\]
This mixing is used at the invariant-amplitude level.  The OPE is first
derived for the basis currents because the two Dirac traces are independent;
the physical amplitudes are then
\[
\widehat\Pi_1=\sin\theta\,\widehat\Pi_A+\cos\theta\,\widehat\Pi_B,\qquad
\widehat\Pi_2=\cos\theta\,\widehat\Pi_A-\sin\theta\,\widehat\Pi_B .
\]
For the pseudoscalar final state,
\[
g_i=
\frac{m_b+m_c}{m_{\Bc}^2 f_{\Bc}\,m_i f_i}
\exp\!\left(\frac{m_i^2}{M_1^2}+\frac{m_{\Bc}^2}{M_2^2}\right)
\widehat\Pi_i^{(P)},
\]
while for the vector final state,
\[
g_i^\ast=
\frac{1}{m_{\Bcst}f_{\Bcst}\,m_i f_i}
\exp\!\left(\frac{m_i^2}{M_1^2}+\frac{m_{\Bcst}^2}{M_2^2}\right)
\widehat\Pi_i^{(V)}.
\]
The updated scripts apply this rotation with physical two-point residues
\(f_1\) and \(f_2\).  The vector \(B_c^\ast\gamma\) entries use the standard
vector-current normalization, with the alternative projector normalization kept
only as a convention check.

The free heavy-quark propagator in momentum space is
\[
S_Q^{(0)}(k)=\frac{i(\Slash{k}+m_Q)}{k^2-m_Q^2+i0},
\qquad Q=c,b .
\]
The hard photon is included by inserting the electromagnetic vertex on either
heavy line:
\[
S_Q^{(\gamma)}(k,k+q)=
S_Q^{(0)}(k+q)\,i e_Q\gamma_\nu\epsilon^\nu\,S_Q^{(0)}(k).
\]
For the \(\bar b\) line it is convenient to use the effective antiquark charge
\(e_{\bar b}=+e/3\), while \(e_c=+2e/3\).  Equivalently, one may keep
\(e_b=-e/3\) and track the orientation of the antiquark line.  The scripts use
\(e_{\bar b}\) explicitly.

Thus, yes: this is the same heavy-heavy propagator logic as in a \(B_c\)-mixing
sum-rule calculation.  The important difference from the strange-sector
radiative calculation is that we do not insert a light-quark photon DA.  If we
later include power corrections, the natural heavy-heavy correction is the
background-gluon expansion of the heavy propagators, e.g. gluon-condensate
terms, not strange-quark condensate photon DAs.

The submitted \(B_c\)-mixing work uses the same local basis,
\[
J_\mu^A=\bar b\gamma_\mu\gamma_5c,\qquad
J_\mu^B=\frac{i}{m_b+m_c}\bar b\sigma_{\mu\alpha}p^\alpha\gamma_5c,
\]
with \(m_b=4.18~\GeV\), \(m_c=1.27~\GeV\), and the final working window
\[
7~\GeV^2\le M^2\le 9~\GeV^2,\qquad
53~\GeV^2\le s_0\le 55~\GeV^2 .
\]
Those are useful starting values for the heavy-heavy OPE in the radiative
problem.  They are not yet automatically the final radiative-transition
windows; the final windows must be fixed by the three-point sum-rule stability,
pole dominance, and convergence tests.

\section{Step-by-Step Sum-Rule Construction}

This section is written as a checklist for reproducing the calculation.

\paragraph{1. Start from basis currents.}
The physical currents \(J_1,J_2\) are mixed combinations of \(J_A,J_B\).  We
derive the OPE for \(J_A\) and \(J_B\) separately only because the Dirac traces
are simpler.  The physical amplitudes are obtained afterward through the
\(\sin\theta,\cos\theta\) rotation.

\paragraph{2. Write the correlators.}
For \(B_c\gamma\),
\[
\Pi_\mu^{(5,K)}(p,q)=
i\int d^4x\,e^{ipx}
\langle\gamma(q,\epsilon)|
T\{\bar b(x)i\gamma_5c(x)\,J_{K\mu}^\dagger(0)\}|0\rangle ,
\qquad K=A,B .
\]
For \(B_c^\ast\gamma\),
\[
\Pi_{\mu\nu}^{(V,K)}(p,q)=
i\int d^4x\,e^{ipx}
\langle\gamma(q,\epsilon)|
T\{\bar b(x)\gamma_\nu c(x)\,J_{K\mu}^\dagger(0)\}|0\rangle .
\]

\paragraph{3. Contract the heavy fields.}
There are two hard-photon diagrams: photon emission from the \(c\) line and
photon emission from the \(\bar b\) line.  The free heavy propagator is
\[
S_Q^{(0)}(k)=\frac{i(\Slash{k}+m_Q)}{k^2-m_Q^2+i0},
\]
and the photon insertion is
\[
S_Q^{(\gamma)}(k,k+q)=
S_Q^{(0)}(k+q)\,i e_Q\Slash{\epsilon}\,S_Q^{(0)}(k).
\]
The charge convention in the scripts is \(e_c=+2/3\) and
\(e_{\bar b}=+1/3\).  No photon DA or light-quark condensate term appears in
this heavy-heavy leading baseline.

\paragraph{4. Evaluate and project the traces.}
For \(B_c\gamma\) project onto
\[
S_{\mu\nu}=p_\nu q_\mu-(p\cdot q)g_{\mu\nu},
\qquad
{\cal P}^{\mu\nu}=\frac{S^{\mu\nu}}{2(p\cdot q)^2},
\qquad
S_{\mu\nu}{\cal P}^{\mu\nu}=1 .
\]
For \(B_c^\ast\gamma\) the current diagnostic tensor is
\[
V_{\mu\nu\rho}=p_\nu\epsilon_{\mu\rho p q}
-(p\cdot q)\epsilon_{\mu\nu\rho p},
\qquad
V_{\mu\nu\rho}V^{\mu\nu\rho}=-4p^2(p\cdot q)^2 .
\]
The vector-channel result still needs matching to the physical
\(1^+\to1^-\gamma\) amplitude basis.

\paragraph{5. Reduce to denominator structures.}
For photon emission from the charm line use
\[
D_1=(k+q)^2-m_c^2,\quad D_2=k^2-m_c^2,\quad
D_3=(k-p)^2-m_b^2.
\]
For photon emission from the anti-bottom line use
\[
D_1=k^2-m_c^2,\quad D_2=(k-p)^2-m_b^2,\quad
D_3=(k-p+q)^2-m_b^2.
\]
The triangle pieces contain the full three-denominator product.  Terms where a
numerator cancels one denominator become two-denominator/contact terms and
must be included or shown to vanish.

\paragraph{6. Borel match and rotate.}
The true variables are \(p^2\) and \(P^2=(p+q)^2\), with
\[
p\cdot q=\frac{P^2-p^2}{2}.
\]
The pilot numerical calculation uses the diagonal choice \(M_1^2=M_2^2=2M^2\),
leading to the practical exponential
\[
\exp\left[\frac{m_i^2+m_f^2}{2M^2}\right].
\]
After obtaining \(\widehat\Pi_A,\widehat\Pi_B\), the physical combinations are
\[
\widehat\Pi_{6743}=\sin\theta\,\widehat\Pi_A+\cos\theta\,\widehat\Pi_B,
\qquad
\widehat\Pi_{6750}=\cos\theta\,\widehat\Pi_A-\sin\theta\,\widehat\Pi_B .
\]
For the \(B_c\gamma\) widths we use
\[
\Gamma(1^+\to0^-\gamma)=
\frac{\alpha_{\rm em}}{3}g^2E_\gamma^3,\qquad
E_\gamma=\frac{m_i^2-m_f^2}{2m_i}.
\]

\section{\texorpdfstring{\(\BcOne\to\Bc\gamma\)}{Bc1 to Bc gamma}: E1 Projection}

For the pseudoscalar final state we project onto
\[
S_{\mu\nu}=p_\nu q_\mu-(p\cdot q)g_{\mu\nu},
\qquad
{\cal P}_{\mu\nu}=\frac{S_{\mu\nu}}{2(p\cdot q)^2}.
\]
FeynCalc gives the normalization check
\[
S_{\mu\nu}{\cal P}^{\mu\nu}=1 .
\]
We denote
\[
p^2=p_2,\qquad p\cdot q=pq .
\]
After rewriting loop scalar products in terms of inverse denominators and
setting those denominators to zero, the projected triangle-core numerators are
\[
\begin{aligned}
C_A^{(c)} &=
-4i\,m_c+\frac{4i\,m_bm_c^2}{pq}-\frac{4i\,m_c^3}{pq},\\
C_A^{(\bar b)} &=
-4i\,m_b+\frac{4i\,m_b^3}{pq}-\frac{4i\,m_b^2m_c}{pq},
\end{aligned}
\]
so that
\[
C_A=e_c C_A^{(c)}+e_{\bar b}C_A^{(\bar b)} .
\]
For the tensor current,
\[
\begin{aligned}
C_B^{(c)} &=
\frac{4i\,m_bm_c-8i\,m_c^2}{m_b+m_c}
-\frac{4i\,m_c^2p_2}{(m_b+m_c)pq},\\
C_B^{(\bar b)} &=
-\frac{4i\,m_bm_c}{m_b+m_c}
-\frac{4i\,m_b^2p_2}{(m_b+m_c)pq},
\end{aligned}
\]
and
\[
C_B=e_c C_B^{(c)}+e_{\bar b}C_B^{(\bar b)} .
\]

The denominator-cancellation terms are stored in the corresponding output file.
They should
not be discarded automatically; they correspond to reduced two-denominator or
contact contributions and must be treated in the dispersion/Borel analysis.

\section{\texorpdfstring{\(\BcOne\to\Bcst\gamma\)}{Bc1 to Bcstar gamma}: Levi-Civita Projection}

For the vector final state a useful gauge-invariant structure is
\[
V_{\mu\nu\rho}
=p_\nu\,\eps_{\mu\rho p q}
-(p\cdot q)\,\eps_{\mu\nu\rho p}.
\]
It is transverse in the photon index for \(q^2=0\).  The FeynCalc checks are
\[
V_{\mu\nu\rho}V^{\mu\nu\rho}=-4p_2(pq)^2,\qquad
V_{\mu\nu\rho}{\cal P}^{\mu\nu\rho}=1 .
\]

The projected \(J_A\) triangle cores are
\[
\begin{aligned}
C_{A,V}^{(c)} &=
-\frac{4i\,m_bm_c}{p_2}
+\frac{2i\,m_c^2}{p_2}
+\frac{4i\,m_c^2}{pq},\\
C_{A,V}^{(\bar b)} &=
-\frac{2i\,m_b^2}{p_2}
+\frac{4i\,m_bm_c}{p_2}
+\frac{4i\,m_b^2}{pq}.
\end{aligned}
\]
The tensor-current vector cores are
\[
\begin{aligned}
C_{B,V}^{(c)} &=
\frac{2i\,m_c}{m_b+m_c}
+\frac{2i\,m_b^2m_c-4i\,m_bm_c^2+2i\,m_c^3}
       {(m_b+m_c)p_2} \\
&\quad
-\frac{4i\,m_bm_c^2-4i\,m_c^3}{(m_b+m_c)pq}
+\frac{2i\,m_c\,pq}{(m_b+m_c)p_2},\\
C_{B,V}^{(\bar b)} &=
\frac{2i\,m_b}{m_b+m_c}
+\frac{-6i\,m_b^3+4i\,m_b^2m_c+2i\,m_bm_c^2}
       {(m_b+m_c)p_2} \\
&\quad
-\frac{4i\,m_b^3-4i\,m_b^2m_c}{(m_b+m_c)pq}
+\frac{2i\,m_b\,pq}{(m_b+m_c)p_2}.
\end{aligned}
\]
Again,
\[
C_{A,V}=e_c C_{A,V}^{(c)}+e_{\bar b}C_{A,V}^{(\bar b)},\qquad
C_{B,V}=e_c C_{B,V}^{(c)}+e_{\bar b}C_{B,V}^{(\bar b)} .
\]

\section{Controlled \texorpdfstring{\(\Bc\gamma\)}{Bc gamma} Pass}

The script
\path{Bc_gamma/scripts/bc_ps_complete_analysis.py}
uses the compact \(B_c\gamma\) triangle cores above and replaces the earlier
common axial-vector normalization by physical two-point residues.  We use the
same central heavy-quark inputs and Borel window as the submitted
\(B_c\)-mixing analysis,
\[
m_b=4.18~\GeV,\qquad m_c=1.27~\GeV,\qquad
\theta=43.3^\circ,
\]
more precisely \(\theta_{\rm mean}=43.295^\circ\) with
\(\sigma_\theta=0.151^\circ\) and \(16\)--\(84\%\) interval
\([43.147^\circ,43.455^\circ]\) from the \(B_c\)-mixing Monte Carlo.  The
updated Monte Carlo samples this \(\theta\) distribution.
\[
M^2=\{7,8,9\}~\GeV^2,\qquad s_0=\{53,54,55\}~\GeV^2.
\]
The pseudoscalar decay-constant benchmark is
\[
f_{\Bc}=0.371\pm0.037~\GeV .
\]
The physical axial-vector residues are extracted from the same two-point
\(B_c\)-mixing basis.  With \(s_\theta=\sin\theta\) and
\(c_\theta=\cos\theta\),
\[
\Pi_1=s_\theta^2\Pi_{AA}+2s_\theta c_\theta\Pi_{AB}
      +c_\theta^2\Pi_{BB},\qquad
\Pi_2=c_\theta^2\Pi_{AA}-2s_\theta c_\theta\Pi_{AB}
      +s_\theta^2\Pi_{BB},
\]
and
\[
f_i(M^2,s_0)=
\left[
\frac{e^{m_i^2/M^2}\Pi_i(M^2,s_0)}{m_i^2}
\right]^{1/2}.
\]
Using the perturbative heavy-heavy two-point spectral densities over the
window above gives
\[
f_1=0.264^{+0.005}_{-0.005}~\GeV,\qquad
f_2=0.722^{+0.016}_{-0.013}~\GeV
\]
from the \(16\)--\(84\%\) grid interval.  This replaces the older common
benchmark \(f_{\BcOne}=0.373~\GeV\).

\begin{table}[h]
\centering
\caption{Updated \(B_c\gamma\) results with physical two-point residues and
the explicitly integrated all-positive dimension-four \(G^2\) sector.  The
quoted intervals are the Monte Carlo \(16\)--\(84\%\) ranges.}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{p{0.24\textwidth}p{0.18\textwidth}p{0.29\textwidth}p{0.15\textwidth}}
\toprule
Channel & Status & Coupling/projection coefficient & \(\Gamma\) (keV)\\
\midrule
\(\BcOne(6743)\to\Bc\gamma\)
& controlled \(B_c\gamma\)
& \(+0.0487\,[0.0414,0.0572]~\GeV^{-1}\)
& \(0.532\,[0.385,0.734]\)\\
\(\BcOne(6750)\to\Bc\gamma\)
& controlled \(B_c\gamma\)
& \(-0.206\,[-0.230,-0.188]~\GeV^{-1}\)
& \(10.04\,[8.29,12.45]\)\\
\bottomrule
\end{tabular}
\end{table}

For the vector final state we also remove the fixed-normalization assumption.
The final-state vector decay constant is defined by
\[
  \langle0|\bar c\gamma_\rho b|\Bcst(p,\eta)\rangle
  =m_{\Bcst}f_{\Bcst}\eta_\rho .
\]
Projecting the two-point vector-current correlator onto the spin--1 invariant
gives the perturbative density
\[
  \rho_V(s)=
  \frac{3}{16\pi^2}\frac{\sqrt{\lambda(s,m_b^2,m_c^2)}}{s}
  \left[
    -\frac{8(k\cdot p)^2}{s}-4m_c^2+12(k\cdot p)+12m_bm_c
  \right],
\]
where \(k\cdot p=(s+m_c^2-m_b^2)/2\).  In the equal-mass limit this reduces to
the expected \(S\)-wave vector-current density proportional to
\((s+2m_Q^2)\sqrt{1-4m_Q^2/s}\).  The corresponding two-point sum rule is
\[
  f_{\Bcst}^2m_{\Bcst}^2e^{-m_{\Bcst}^2/M_V^2}
  =
  \int_{(m_b+m_c)^2}^{s_{0,V}}ds\,e^{-s/M_V^2}\rho_V(s).
\]
Using \(M_V^2=5\)--\(8~\GeV^2\) and \(s_{0,V}=40\)--\(44~\GeV^2\), the direct
spin-projector density gives
\[
  f_{\Bcst}^{\rm projector}=0.753\,[0.693,0.808]~\GeV .
\]
This is a projector-convention diagnostic.  For the physical matrix element
\(\langle0|\bar c\gamma_\rho b|\Bcst\rangle=m_{\Bcst}f_{\Bcst}\eta_\rho\), the
standard vector-invariant convention divides the density by the transverse
spin-trace factor of three.  The corresponding self-contained two-point result
is
\[
  f_{\Bcst}^{\rm standard}=0.435\,[0.400,0.467]~\GeV .
\]
This is close to the commonly used reference value
\(f_{\Bcst}=0.384\pm0.038~\GeV\).  We therefore quote the standard
normalization as the preferred self-contained result and keep the reference
normalization as a sensitivity check:

\begin{table}[h]
\centering
\caption{Hard-QCDSR \(B_c^\ast\gamma\) predictions.  The standard
vector-invariant entries include the perturbative hard-photon three-point term,
the physical \(f_1,f_2\) residues, and the explicitly integrated all-positive
dimension-four \(G^2\) sector.  The reference-normalization rows are retained as
perturbative sensitivity checks.}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{p{0.24\textwidth}p{0.24\textwidth}p{0.27\textwidth}p{0.15\textwidth}}
\toprule
Channel & Normalization & Coupling/projection coefficient & \(\Gamma\) (keV)\\
\midrule
\(\BcOne(6743)\to\Bcst\gamma\)
& standard vector-invariant \(f_{\Bcst}\)
& \(-0.0764\,[-0.0821,-0.0717]~\GeV^{-1}\)
& \(70.3\,[61.9,81.2]\)\\
\(\BcOne(6750)\to\Bcst\gamma\)
& standard vector-invariant \(f_{\Bcst}\)
& \(+0.173\,[0.161,0.185]~\GeV^{-1}\)
& \(382\,[331,437]\)\\
\(\BcOne(6743)\to\Bcst\gamma\)
& reference \(f_{\Bcst}=0.384\pm0.038~\GeV\)
& \(-0.0877\,[-0.0986,-0.0795]~\GeV^{-1}\)
& \(92.6\,[76.1,117]\)\\
\(\BcOne(6750)\to\Bcst\gamma\)
& reference \(f_{\Bcst}=0.384\pm0.038~\GeV\)
& \(+0.187\,[0.169,0.210]~\GeV^{-1}\)
& \(447\,[365,564]\)\\
\bottomrule
\end{tabular}
\end{table}

The \(\Bc\gamma\) entries are the controlled hard-photon baseline from the
present calculation.  The vector entries are no longer just placeholders:
they use the \(V_{\mu\nu\rho}\) projection, the physical \(f_1,f_2\) residues,
and an explicit \(f_{\Bcst}\) normalization.  The projector diagnostic gives
\(24.8[21.8,28.5]\) and \(120[104,137]\) keV for the two vector channels and is
kept only in the output CSV files as a convention check.  The table above uses
the standard vector-current convention.  After the all-positive \(G^2\)
integration below, these entries become the preferred final vector predictions;
the projector diagnostic remains only a normalization check.

The vector stability plots are generated by
\texttt{bc\_vec\_complete\_analysis.py}.  On the central \(3\times3\)
\((M^2,s_0)\) grid, the standard-normalization widths vary from about
\(66.7\) to \(80.9~\mathrm{keV}\) for \(\BcOne(6743)\to\Bcst\gamma\), and from about
\(310\) to \(406~\mathrm{keV}\) for \(\BcOne(6750)\to\Bcst\gamma\).  The large higher
state width is therefore not a numerical instability of the selected Borel
window.

Before the explicit all-positive calculation was completed, we used the same
conservative screening logic as in the \(\Bc\gamma\) channel, but with one additional
residue factor.  The vector sum rule contains \(f_i f_{\Bcst}\) in the
denominator, so
\[
  \left|\frac{\delta g}{g}\right|
  \lesssim
  \left|\frac{\delta\Pi^{(3)}}{\Pi^{(3)}}\right|
  +
  \left|\frac{\delta f_i}{f_i}\right|
  +
  \left|\frac{\delta f_{\Bcst}}{f_{\Bcst}}\right|
  \simeq
  2\,\max\left|\frac{\Pi_{G^2}}{\Pi_{\rm pert}}\right|,
\]
and
\[
  \left|\frac{\delta\Gamma}{\Gamma}\right|
  \lesssim
  4\,\max\left|\frac{\Pi_{G^2}}{\Pi_{\rm pert}}\right|.
\]
For the preferred standard vector normalization this gives the screening
envelopes
\[
\begin{array}{c|cc}
\text{channel} & \text{median envelope} & \text{maximum envelope}\\
\hline
\BcOne(6743)\to\Bcst\gamma & \pm 11.1~\mathrm{keV} & \pm 27.7~\mathrm{keV}\\
\BcOne(6750)\to\Bcst\gamma & \pm 53.6~\mathrm{keV} & \pm 139~\mathrm{keV}
\end{array}
\]
for the widths.  This was not an explicit condensate correction; it is retained
only as a diagnostic explaining why the all-positive \(G^2\) sector was
computed.  The refined contact audit below shows that the contact rows do not
have ordinary physical two-channel support; the crossed rows are retained only
as an audit trail.

\section{Comparison with Experiment and Other Theory}

LHCb has observed a wide peaking structure in the \(\Bc^+\gamma\) mass
spectrum with significance above seven standard deviations.  A minimal
two-peak description gives~\cite{LHCbBc1PObservation2025,LHCbBc1PStudy2025}
\[
M_1=6704.8\pm5.5\pm2.8\pm0.3~{\rm MeV},\qquad
M_2=6752.4\pm9.5\pm3.1\pm0.3~{\rm MeV},
\]
where the errors are statistical, systematic, and due to the \(B_c^+\) mass.
No individual radiative partial width is measured.  The natural widths are
expected to be only a few hundred keV and are neglected in the experimental
fit because they are small compared with the photon-energy resolution.

\begin{table}[h]
\centering
\caption{Qualitative comparison with the current experimental information
from LHCb~\cite{LHCbBc1PObservation2025,LHCbBc1PStudy2025}.}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lll}
\toprule
Quantity & Experiment & Present input/result\\
\midrule
Observed \(B_c(1P)^+\)-like signal
& yes, \(>7\sigma\) in \(\Bc^+\gamma\)
& channels studied explicitly\\
Lower visible peak
& \(6704.8\pm5.5\pm2.8\pm0.3~{\rm MeV}\)
& input state \(6743~{\rm MeV}\)\\
Higher visible peak
& \(6752.4\pm9.5\pm3.1\pm0.3~{\rm MeV}\)
& input state \(6750~{\rm MeV}\)\\
Partial widths
& not measured
& \(\Bc\gamma\): \(0.532\), \(10.04~{\rm keV}\);
  \(\Bcst\gamma\): \(70.3\), \(382~{\rm keV}\)\\
\bottomrule
\end{tabular}
\end{table}

The lower visible peak should not be identified one-to-one with the input
\(6743~{\rm MeV}\) state without care.  In the measured \(\Bc\gamma\) spectrum,
decays through \(\Bcst\gamma\), followed by an unreconstructed soft
\(\Bcst\to\Bc\gamma\), can shift visible peaks by the unknown hyperfine
splitting.

For comparison with other theory we should not compress different papers into
a single range.  Table~\ref{tab:bc1-radiative-comparison} lists each quoted
calculation separately.  The entries are the values collected in
Bondar--Milstein~\cite{BondarMilstein2025}; the original model papers are
cited in the first column.

\begin{table}[h]
\centering
\caption{Comparison with representative predictions for
\(B_{c1}\to B_c^{(\ast)}\gamma\).  Widths are in keV.}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{p{0.25\textwidth}rrrr}
\toprule
Publication
& \(6743\to B_c\gamma\)
& \(6743\to B_c^\ast\gamma\)
& \(6750\to B_c\gamma\)
& \(6750\to B_c^\ast\gamma\)\\
\midrule
Godfrey~\cite{Godfrey2004} & 13 & 60 & 80 & 11\\
Ebert--Faustov--Galkin~\cite{Ebert2003} & 18.4 & 78.9 & 132 & 13.6\\
Fulcher~\cite{Fulcher1999} & 32.4 & 75.6 & 127.8 & 26.2\\
Gershtein et al.~\cite{Gershtein1995} & 11.6 & 77.8 & 131.1 & 8.1\\
T. Y. Li et al.~\cite{LiTang2023} & 16.6 & 49 & 66.6 & 10.5\\
Q. Li et al.~\cite{LiZhong2019} & 35 & 70 & 74 & 40\\
X. J. Li et al.~\cite{LiLiu2023} & 30.1 & 47.8 & 64 & 25.6\\
Eichten--Quigg~\cite{EichtenQuigg2018} & 9.9 & 62.5 & 92.3 & 7.5\\
Bondar--Milstein~\cite{BondarMilstein2025} & 22 & 75 & 47 & 2\\
This work & \(0.532[0.385,0.734]\) & \(70.3[61.9,81.2]\)
& \(10.04[8.29,12.45]\) & \(382[331,437]\)\\
\bottomrule
\end{tabular}
\label{tab:bc1-radiative-comparison}
\end{table}

Thus the \(\Bc\gamma\) and \(\Bcst\gamma\) channels are controlled hard-QCDSR
predictions including the explicitly integrated all-positive \(G^2\) sector.
The contact-support audits leave no ordinary two-channel contact contribution
to add to the standard physical double-Borel sum.

\section{Perturbative and Condensate Content}

The \(B_c\gamma\) numerical table above contains the leading hard-photon
perturbative three-point baseline, normalized with perturbative two-point
physical residues.  In practical terms this means:
\begin{itemize}
  \item the photon is emitted from the charm or anti-bottom heavy-quark line;
  \item both heavy propagators are free propagators in the radiative
  three-point OPE;
  \item the retained spectral density is the perturbative triangle hard
  contribution generated by the projected Dirac traces;
  \item no photon DA, \(\chi\langle\bar q q\rangle\), or light-quark condensate
  contribution appears, because there is no light valence quark in \(B_c\);
  \item gluon-condensate corrections from the background-gluon expansion of the
  heavy propagators are included through the explicit all-positive \(G^2\)
  sector;
  \item reduced two-denominator/contact terms from denominator cancellation
  have been audited in the vector \(B_c^\ast\gamma\) channel and do not give
  ordinary two-channel double-pole contributions.
\end{itemize}
Thus the present \(B_c\gamma\) and \(B_c^\ast\gamma\) results are best described
as controlled hard-QCDSR predictions with the explicit all-positive \(G^2\)
sector included.  The contact audits leave only crossed-contact or
single-virtuality candidates outside the standard two-channel projection.

\section{Dimension-4 Radiative Gluon-Condensate Workbench}

The heavy-heavy \(B_c\) system has no photon DA or light-quark condensate
contribution, but the background-gluon expansion of the heavy propagators
generates possible dimension-4 gluon-condensate corrections to the radiative
three-point function.  To keep the calculation reproducible, the
\(\langle\alpha_s G^2/\pi\rangle\) part was split into small FeynCalc chunks
instead of reducing one very large trace.

For the \(\Bc\gamma\) E1 structure the two hard-photon topologies are
\[
S_c(k+q)\gamma_{\rm em}S_c(k)\gamma_5S_b(k-p),
\qquad
S_c(k)\gamma_5S_b(k-p)\gamma_{\rm em}S_b(k-p+q).
\]
In each topology we considered
\begin{itemize}
  \item one single-line insertion \(S_Q^{(G^2)}\) on each heavy propagator
  segment;
  \item one open-gluon-pair insertion \(S^{(G)}S^{(G)}\) for each pair of
  propagator segments.
\end{itemize}
Thus there are six single-line topologies and six open-pair topologies.  Each
topology is evaluated for the two basis currents \(J_A\) and \(J_B\), giving
24 projected numerator rows in total.

The projection uses
\[
S_{\mu\nu}=p_\nu q_\mu-(p\cdot q)g_{\mu\nu},\qquad
{\cal P}^{\mu\nu}=\frac{S^{\mu\nu}}{2(p\cdot q)^2},
\]
so that the projected coefficient is the coefficient of the same E1 tensor
used in the perturbative baseline.  With the present conventions the audit is
\[
\begin{array}{lcc}
\hline
\hbox{class} & \hbox{current-split rows} & \hbox{projected terms}\\
\hline
S_Q^{(G^2)} & 12 & 221\\
S^{(G)}S^{(G)} & 12 & 164\\
\hline
\hbox{total} & 24 & 385\\
\hline
\end{array}
\]

The scripts which generate these checks are
\begin{itemize}
  \item \path{Bc_gamma/scripts/step3_ps_g2_topology_inventory.py};
  \item \path{Bc_gamma/scripts/step3_ps_g2_single_line_cphoton.wl};
  \item \path{Bc_gamma/scripts/step3_ps_g2_single_line_bbarphoton.wl};
  \item \path{Bc_gamma/scripts/step3_ps_g2_open_pair_cphoton.wl};
  \item \path{Bc_gamma/scripts/step3_ps_g2_open_pair_bbarphoton.wl};
  \item \path{Bc_gamma/scripts/step3_ps_g2_projection_summary.py};
  \item \path{Bc_gamma/scripts/step3_ps_g2_denominator_bookkeeping.py}.
\end{itemize}
The raw outputs are stored in
\path{Bc_gamma/outputs/step3_ps_g2_*.txt} and the summary table is stored in
\path{Bc_gamma/outputs/step3_ps_g2_projection_summary.csv}.  The denominator
manifest is stored in
\path{Bc_gamma/outputs/step3_ps_g2_denominator_bookkeeping.csv}.

The denominator bookkeeping is most compact in Schwinger parameters.  For the
charm-line photon topology we use
\[
a\leftrightarrow S_c(k+q),\qquad
b\leftrightarrow S_c(k),\qquad
r\leftrightarrow S_b(k-p),\qquad A=a+b+r .
\]
After shifting the loop momentum the quadratic form is
\[
\Phi_c=
\frac{r(a+b)}{A}p^2+\frac{2ar}{A}(p\cdot q)
-(a+b)m_c^2-rm_b^2
=
\frac{rb}{A}p^2+\frac{ar}{A}P^2-(a+b)m_c^2-rm_b^2 .
\]
For the anti-bottom-line photon topology we use
\[
a\leftrightarrow S_c(k),\qquad
b\leftrightarrow S_b(k-p),\qquad
r\leftrightarrow S_b(k-p+q),\qquad A=a+b+r ,
\]
which gives
\[
\Phi_{\bar b}=
\frac{a(b+r)}{A}p^2+\frac{2r(b+r)}{A}(p\cdot q)
-a m_c^2-(b+r)m_b^2 .
\]
Equivalently, since \(P^2=p^2+2p\cdot q\),
\[
\Phi_{\bar b}=
\frac{(b+r)(a-r)}{A}p^2+\frac{r(b+r)}{A}P^2
-a m_c^2-(b+r)m_b^2 .
\]
For \(S_Q^{(G^2)}\), the selected propagator power is four and the other two
propagator powers are one.  For \(S^{(G)}S^{(G)}\), the selected pair carries
powers two and two, while the remaining propagator has power one.

This completes the numerator-projection stage of the radiative
gluon-condensate workbench and attaches denominator powers to each projected
row.  It is not yet a numerical condensate correction to the decay width.  The
next step is to perform the double-dispersion/double-Borel reduction and
integrate the result over the same Borel and continuum-threshold windows used
for the perturbative baseline.

\subsection*{Conservative \(G^2\) Size Screen}

Before completing the full derivative-delta reduction, we performed a
conservative size screen using the completed \(B_c\)-mixing OPE convergence
table in the same numerical window,
\[
M^2=\{7,8,9\}\,\GeV^2,\qquad
s_0=\{53,54,55\}\,\GeV^2 .
\]
The script is \path{bc_ps_g2_screening_estimate.py}.  The corresponding CSV
and text outputs are stored in the \path{Bc_gamma/outputs} directory.

The screen defines
\[
\Delta_{\rm 2pt}^{G^2}=
\max\left(
\left|\frac{\Pi_{AA}^{G^2}}{\Pi_{AA}^{\rm pert}}\right|,
\left|\frac{\Pi_{AB}^{G^2}}{\Pi_{AB}^{\rm pert}}\right|,
\left|\frac{\Pi_{BB}^{G^2}}{\Pi_{BB}^{\rm pert}}\right|
\right)
\]
from the \(B_c\)-mixing calculation.  Since \(f\sim\sqrt{\Pi}\), the
normalization shift is estimated as
\(\Delta_f\simeq \Delta_{\rm 2pt}^{G^2}/2\).  Taking the unknown radiative
three-point \(G^2\) shift to be of the same size gives the conservative
envelope
\[
\left|\frac{\delta g}{g}\right|_{\rm env}
=\Delta_{\rm 2pt}^{G^2}+\frac{1}{2}\Delta_{\rm 2pt}^{G^2},
\qquad
\left|\frac{\delta\Gamma}{\Gamma}\right|_{\rm env}
\simeq 2\left|\frac{\delta g}{g}\right|_{\rm env}.
\]
Numerically this gives a median conservative envelope
\(|\delta g/g|_{\rm env}=0.058\) and
\(|\delta\Gamma/\Gamma|_{\rm env}=0.115\), with maxima \(0.128\) and \(0.257\),
respectively, over the grid.

Therefore the screen was not small enough to justify silently dropping
\(G^2\) at publication level.  It did not prove that the radiative
three-point \(G^2\) correction was as large as the envelope; it showed that a
few-percent amplitude effect was plausible in the same heavy-heavy OPE window.
This diagnostic is superseded by the explicit all-positive \(G^2\) integration
below.

The channel-by-channel conservative envelope is summarized in
Table~\ref{tab:bc-g2-envelope}.  The table is generated by
\path{bc_ps_g2_corrected_summary.py} and should be interpreted as a systematic
bound, not as the final explicit radiative \(G^2\) contribution.

\begin{table}[h]
\centering
\caption{Perturbative \(B_{c1}\to B_c\gamma\) result with conservative
\(G^2\) width envelope.  Widths are in keV; the last column gives
median/max envelope sizes.}
\small
\begin{tabular}{lccc}
\hline
Channel & \(g_{\rm pert}\,[\GeV^{-1}]\) & \(\Gamma_{\rm pert}\) &
\(G^2\) env.\\
\hline
\(B_{c1}(6743)\to B_c\gamma\) &
\(0.0316[0.0269,0.0370]\) &
\(0.223[0.162,0.308]\) &
\(\pm0.025/\pm0.060\)\\
\(B_{c1}(6750)\to B_c\gamma\) &
\(-0.184[-0.205,-0.167]\) &
\(8.01[6.60,9.90]\) &
\(\pm0.914/\pm2.30\)\\
\hline
\end{tabular}
\label{tab:bc-g2-envelope}
\end{table}

\subsection*{Denominator-Reduced \(G^2\) Inventory}

To test whether the full explicit radiative \(G^2\) correction could be
obtained from ordinary positive-power Schwinger integrals alone, we reduced
the projected \(G^2\) numerators in inverse propagator denominators
\(d_1,d_2,d_3\).  This is done by
\path{step3_ps_g2_denominator_reduction.wl}; the summary is generated by
\path{step3_ps_g2_denominator_reduction_summary.py}.

The complete reduction contains 747 terms.  Of these, 375 have all effective
denominator powers positive, while 372 terms have at least one nonpositive
effective power and therefore belong to the contact/derivative sector.  Thus
the latter sector is not a small correction to the bookkeeping; it is roughly
half of the denominator-reduced expression.

Consequently, an integration of only the all-positive sector would not be
defensible without auditing the contact sector.  The refined audit below shows
that the contact rows do not carry ordinary two-channel double-Borel support,
so the final explicit numerical correction is the all-positive sector reported
in the next section.

\subsection*{\texorpdfstring{\(\Bcst\gamma\)}{Bcstar gamma}
Denominator-Reduced \(G^2\) Inventory}

The same denominator-reduction audit was carried out for the vector final
state.  The projected structure is
\[
  V_{\mu\nu\rho}
  =
  p_\nu\epsilon_{\mu\rho pq}
  -
  (p\cdot q)\epsilon_{\mu\nu\rho p},
  \qquad
  V_{\mu\nu\rho}V^{\mu\nu\rho}=-4p^2(p\cdot q)^2 .
\]
The script \path{step3_vec_g2_denominator_reduction.wl} replaces the
appropriate propagator numerators by \(S_Q^{(G^2)}\) or by open one-gluon
pieces \(S_Q^{(G)}S_{Q'}^{(G)}\), projects onto \(V_{\mu\nu\rho}\), and rewrites
the result in powers of \(d_1,d_2,d_3\).  The summary script is
\path{step3_vec_g2_denominator_reduction_summary.py}.

The complete vector reduction contains 1095 terms:
\[
\begin{array}{c|c}
\text{sector} & \text{number of terms}\\
\hline
\text{all-positive denominator powers} & 538\\
\text{contact/derivative sector} & 557
\end{array}
\]
By current, the split is
\[
\begin{array}{c|cc}
\text{current} & \text{all-positive} & \text{contact/derivative}\\
\hline
J^A_\mu & 200 & 148\\
J^B_\mu & 338 & 409
\end{array}
\]
and by background-field class it is
\[
\begin{array}{c|cc}
\text{class} & \text{all-positive} & \text{contact/derivative}\\
\hline
\text{single-line }G^2 & 209 & 368\\
\text{open-pair }GG & 329 & 189
\end{array}.
\]
Thus the contact/derivative sector is slightly larger than the ordinary
positive-denominator sector in the vector channel.  This is why the
\(\Bcst\gamma\) result should be quoted as a leading perturbative vector
baseline with a \(G^2\)/contact systematic screen, rather than as a completed
full-OPE prediction.

The support-level double-Borel audit is performed by
\path{step3_vec_g2_contact_support_audit.py}.  It first separates contact rows
that contain both hadronic virtualities from rows that are single-virtuality or
no-external-virtuality subtraction terms.  The first-pass result is
\[
\begin{array}{c|c}
\text{contact support class} & \text{number of rows}\\
\hline
\text{double-Borel-active candidates} & 131\\
\text{single-virtuality rows} & 309\\
\text{no-external-virtuality rows} & 117
\end{array}
\]
All 131 first-pass active candidates come from the anti-bottom photon topology
with remaining denominator support \(\{d_1,d_3\}\).  This needs one more
physical-support check.  In that topology
\[
d_1=k^2-m_c^2,\qquad d_3=(k-p+q)^2-m_b^2 .
\]
Combining only \(d_1\) and \(d_3\) with Schwinger parameters gives an external
piece proportional to
\[
 \frac{t_1t_3}{t_1+t_3}\left[-P^2+2p^2\right]
 =
 \frac{t_1t_3}{t_1+t_3}(p-q)^2,
 \qquad P=p+q,\quad q^2=0 .
\]
Thus the two-denominator contact candidate depends on the crossed virtuality
\((p-q)^2\), not on independent physical initial- and final-channel pole
variables.  The refined audit
\path{step3_vec_g2_contact_borel_admissibility.py} gives
\[
\begin{array}{c|c}
\text{refined contact support class} & \text{number of rows}\\
\hline
\text{crossed single-combination rows} & 131\\
\text{single-virtuality rows} & 309\\
\text{no-external-virtuality rows} & 117\\
\text{ordinary two-channel contact rows} & 0
\end{array}
\]
Therefore no contact/derivative row is added directly to the physical
double-pole numerical sum in the standard two-channel Borel projection.  The
131 crossed rows are stored in
\path{step3_vec_g2_contact_active_candidates.csv} as an audit trail; they would
require a separate crossed-contact prescription before being used in a
numerical width.

For a student checking this calculation, the most useful debugging sequence is:
\begin{enumerate}
  \item verify the projector normalization
  \(V_{\mu\nu\rho}V^{\mu\nu\rho}=-4p^2(p\cdot q)^2\);
  \item reproduce one \(J^A_\mu\) single-line insertion before running all
  topologies;
  \item check the denominator substitutions separately for charm-photon and
  anti-bottom-photon emission;
  \item classify terms with effective powers \(n_i>0\) as ordinary Schwinger
  terms and terms with at least one \(n_i\le0\) as contact/derivative terms;
  \item run the support audit, then the refined Borel-admissibility audit;
  \item check that the apparent 131 active rows all reduce to crossed
  \((p-q)^2\) support;
  \item keep these rows in the audit trail, but do not add them to the
  physical double-pole sum unless a separate crossed-contact prescription is
  introduced.
\end{enumerate}

\section{Explicit All-Positive \texorpdfstring{\(G^2\)}{G2} Integration}

The old screening estimate is now superseded by the explicit all-positive
dimension-four calculation.  After reducing the projected \(G^2\) numerators in
inverse denominator powers \(d_1,d_2,d_3\), the ordinary part is the sector with
\[
  n_1>0,\qquad n_2>0,\qquad n_3>0 .
\]
These rows have standard Schwinger representations and are Borel transformed
directly.  The pseudoscalar channel contains 375 such terms and the vector
channel contains 538 such terms.

The heavy-heavy convention is the same as in the submitted \(B_c\)-mixing
analysis:
\[
  S_Q^{(G^2)}:\ \frac{G^2}{12},\qquad
  S_Q^{(G)}S_{Q'}^{(G)}:\ \frac{G^2}{96}\frac{N_c^2-1}{2},\qquad N_c=3 .
\]
The direct numerical check uses the diagonal double-Borel relation
\[
  M_1^2=M_2^2=2M^2 ,
\]
fixes \(p^2=m_f^2\), and uses
\[
  p\cdot q=\frac{m_i^2-m_f^2}{2}
\]
for each physical initial state.  The scripts are
\path{bc_ps_g2_all_positive_direct_borel.py},
\path{bc_ps_g2_all_positive_mc_update.py},
\path{bc_vec_g2_all_positive_direct_borel.py}, and
\path{bc_vec_g2_all_positive_mc_update.py}.

The pseudoscalar contact audit gives
\[
\begin{array}{c|c}
\text{refined contact support class} & \text{number of rows}\\
\hline
\text{crossed single-combination rows} & 80\\
\text{single-physical-virtuality rows} & 220\\
\text{no-external-virtuality rows} & 72\\
\text{ordinary two-channel contact rows} & 0
\end{array}
\]
Together with the vector audit above, this means that no contact/derivative row
is added to the standard physical double-Borel sum.

The all-positive \(G^2\) correction shifts the couplings by
\[
\begin{array}{c|c}
\text{channel} & \delta g/g\ \text{from}\ G^2_{\rm ap}\\
\hline
\BcOne(6743)\to\Bc\gamma & +0.543[+0.537,+0.546]\\
\BcOne(6750)\to\Bc\gamma & +0.120[+0.112,+0.130]\\
\BcOne(6743)\to\Bcst\gamma & -0.0245[-0.0328,-0.0190]\\
\BcOne(6750)\to\Bcst\gamma & +0.0298[+0.0264,+0.0347]
\end{array}
\]
and gives the final Monte Carlo-folded results
\[
\begin{array}{c|c|c}
\text{channel} & g & \Gamma~({\rm keV})\\
\hline
\BcOne(6743)\to\Bc\gamma & +0.0487[0.0414,0.0572]~{\rm GeV}^{-1} & 0.532[0.385,0.734]\\
\BcOne(6750)\to\Bc\gamma & -0.206[-0.230,-0.188]~{\rm GeV}^{-1} & 10.04[8.29,12.45]\\
\BcOne(6743)\to\Bcst\gamma & -0.0764[-0.0821,-0.0717]~{\rm GeV}^{-2} & 70.3[61.9,81.2]\\
\BcOne(6750)\to\Bcst\gamma & +0.173[0.161,0.185]~{\rm GeV}^{-2} & 382[331,437]
\end{array}
\]

\section{Vector Projector and Width Normalization Audit}

The vector tensor used in the projection,
\[
V_{\mu\nu\rho}
=p_\nu\epsilon_{\mu\rho pq}
-(p\cdot q)\epsilon_{\mu\nu\rho p},
\]
has mass dimension three.  Consequently the coefficient extracted from the
sum rule, denoted here by \(g_V\), has dimension \({\rm GeV}^{-2}\), not
\({\rm GeV}^{-1}\).  The script
\path{bc_vec_projector_width_audit.py} performs the explicit polarization
sum and gives
\[
\frac{1}{3}\sum_{\rm pol}
|\eta_A^\mu\epsilon_\gamma^\nu\eta_V^\rho V_{\mu\nu\rho}|^2
=
\frac{2}{3}m_i^2E_\gamma^2(2m_f^2+E_\gamma^2).
\]
The vector-width formula used in the numerical code is therefore
\[
\Gamma(1^+\to1^-\gamma)
=
\frac{\alpha_{\rm em}}{3}g_V^2(2m_f^2+E_\gamma^2)E_\gamma^3.
\]
If one wants the same one-momentum E1 convention as in
\(\Gamma=\alpha_{\rm em}g_{E1}^2E_\gamma^3/3\), then
\[
g_{E1}=\sqrt{2m_f^2+E_\gamma^2}\,g_V.
\]
Numerically the conversion factor is \(8.969\) for both vector channels, giving
\[
\begin{array}{c|cc}
\text{channel} & g_V~({\rm GeV}^{-2}) & g_{E1}~({\rm GeV}^{-1})\\
\hline
\BcOne(6743)\to\Bcst\gamma
& -0.0764[-0.0821,-0.0717] & -0.685[-0.736,-0.643]\\
\BcOne(6750)\to\Bcst\gamma
& +0.173[0.161,0.185] & +1.55[1.45,1.66]
\end{array}
\]
Thus the projector and width normalization are internally consistent.  The
large \(6750/6743\) vector hierarchy is not caused by a width-conversion factor;
it comes from the mixed-current vector amplitude and should be checked through
the separate sign, current-assignment, and no-mixing-limit audits.

\section{Reproduction Checklist for the Present Pilot}

The current numbers can be reproduced in the following order.
\begin{enumerate}
  \item Run \path{Bc_gamma/scripts/step1_hard_photon_numerators.wl}.  This
  computes the raw FeynCalc traces for photon emission from the charm line and
  from the anti-bottom line.
  \item Run \path{Bc_gamma/scripts/step2_ps_e1_triangle_reduction.wl}.  This
  projects the \(B_c\gamma\) traces onto
  \(S_{\mu\nu}=p_\nu q_\mu-(p\cdot q)g_{\mu\nu}\) and checks
  \(S_{\mu\nu}{\cal P}^{\mu\nu}=1\).
  \item Run \path{Bc_gamma/scripts/step2_vec_epsilon_A_reduction.wl} and
  \path{Bc_gamma/scripts/step2_vec_epsilon_B_reduction.wl}.  These produce the
  diagnostic \(B_c^\ast\gamma\) cores and check the normalization of
  \(V_{\mu\nu\rho}\).
  \item Insert the compact projected cores into
  \path{Bc_gamma/scripts/bc_ps_complete_analysis.py}.  The script uses the
  diagonal calibration \(M_1^2=M_2^2=2M^2\), with
  \(M^2=\{7,8,9\}\,\GeV^2\) and \(s_0=\{53,54,55\}\,\GeV^2\).
  \item Extract \(f_1\) and \(f_2\) from the diagonalized two-point
  perturbative moments and then sample \(m_b,m_c,M^2,s_0,\theta\), and
  \(f_{B_c}\) in the Monte Carlo.
  \item Rotate the basis amplitudes with
  \(\widehat\Pi_{6743}=\sin\theta\,\widehat\Pi_A+\cos\theta\,\widehat\Pi_B\)
  and
  \(\widehat\Pi_{6750}=\cos\theta\,\widehat\Pi_A-\sin\theta\,\widehat\Pi_B\).
  \item Run the all-positive \(G^2\) direct-Borel scripts and fold the median
  \(\delta g/g\) correction into the same Monte Carlo ensemble.
  \item Convert the final couplings to widths using
  \[
  \Gamma(1^+\to0^-\gamma)=
  \frac{\alpha_{\rm em}}{3}g^2
  \left(\frac{m_i^2-m_{\Bc}^2}{2m_i}\right)^3 .
  \]
\end{enumerate}
At this stage both the \(B_c\gamma\) and \(B_c^\ast\gamma\) entries include the
explicit all-positive \(G^2\) sector.  The contact audits show no ordinary
two-channel contact contribution; crossed-contact rows are kept separately as a
consistency check.

\section{Double-Dispersion Denominator Check}

The double-dispersion variables satisfy
\[
P^2=p^2+2p\cdot q,\qquad pq=\frac{P^2-p^2}{2}.
\]
For \(\Bc\gamma\), the structure is close to the strange-sector E1 case, but
with two heavy masses.  For \(\Bcst\gamma\), the additional \(1/p_2\) and
\(pq/p_2\) structures make the double-dispersion bookkeeping a useful
independent check of the diagonal Borel implementation.

\subsection*{Double-dispersion denominator}

For the photon emitted from the charm line, the three denominators are
\[
D_1=(k+q)^2-m_c^2,\qquad
D_2=k^2-m_c^2,\qquad
D_3=(k-p)^2-m_b^2 .
\]
With Feynman parameters \(x,y,z\), \(x+y+z=1\), the combined denominator is
\[
xD_1+yD_2+zD_3
=\ell^2-\Delta_c,
\]
where
\[
\Delta_c=(1-z)m_c^2+z m_b^2-zy\,p^2-xz\,P^2 .
\]
For photon emission from the \(\bar b\) line, using the momentum routing in the
FeynCalc scripts,
\[
D_1=k^2-m_c^2,\qquad
D_2=(k-p)^2-m_b^2,\qquad
D_3=(k-p+q)^2-m_b^2 ,
\]
and the analogous reduction gives, with \(x+y+z=1\),
\[
\Delta_{\bar b}
=x m_c^2+(1-x)m_b^2-x(1-x)p^2+xz(P^2-p^2).
\]
Equivalently one may relabel the Feynman parameters after choosing a different
loop momentum.  These forms make clear why the true radiative problem is a
double-dispersion problem in \(p^2\) and \(P^2\), not simply the two-point mixing
correlator with an extra charge factor.

\begin{thebibliography}{9}

\bibitem{LHCbBc1PObservation2025}
R. Aaij et al. (LHCb Collaboration),
``Observation of Orbitally Excited \(B_c^+\) States,''
Phys. Rev. Lett. 135, 231902 (2025).

\bibitem{LHCbBc1PStudy2025}
R. Aaij et al. (LHCb Collaboration),
``Study of \(B_c(1P)^+\) states in the \(B_c^+\gamma\) mass spectrum,''
Phys. Rev. D 112, 112003 (2025).

\bibitem{MartinGonzalez2022}
B. Martín-González, P. G. Ortega, D. R. Entem,
F. Fernández, and J. Segovia,
``Towards the discovery of novel \(B_c\) states: radiative and hadronic
transitions,''
arXiv:2205.05950.

\bibitem{BondarMilstein2025}
A. E. Bondar and A. I. Milstein,
``Phenomenology of \(D_{s1}\) mesons radiative transitions,''
Phys. Rev. D 111, 114019 (2025).

\bibitem{Godfrey2004}
S. Godfrey,
Phys. Rev. D 70, 054017 (2004).

\bibitem{Ebert2003}
D. Ebert, R. N. Faustov, and V. O. Galkin,
Phys. Rev. D 67, 014027 (2003).

\bibitem{Fulcher1999}
L. P. Fulcher,
Phys. Rev. D 60, 074006 (1999).

\bibitem{Gershtein1995}
S. S. Gershtein, V. V. Kiselev, A. K. Likhoded, and A. V. Tkabladze,
Phys. Rev. D 51, 3613 (1995).

\bibitem{LiTang2023}
T. Y. Li, L. Tang, Z. Y. Fang, C. H. Wang, C. Q. Pang, and X. Liu,
Phys. Rev. D 108, 034019 (2023).

\bibitem{LiZhong2019}
Q. Li, M. S. Liu, L. S. Lu, Q. F. Lü, L. C. Gui, and X. H. Zhong,
Phys. Rev. D 99, 096020 (2019).

\bibitem{LiLiu2023}
X. J. Li, Y. S. Li, F. L. Wang, and X. Liu,
Eur. Phys. J. C 83, 1080 (2023).

\bibitem{EichtenQuigg2018}
E. J. Eichten and C. Quigg,
Phys. Rev. D 99, 054025 (2018).

\end{thebibliography}

\end{document}
